---
output: html_fragment
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Cross-Sectional Data
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
## Inference {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 7.3
</p>

The dataset contains data on test performance, school characteristics and student demographic backgrounds for school districts in California with 420 observations on 14 variables. We calculate a linear regression with the average math and reading score as the dependent variable. We want to test if the student teacher ratio and the expenditure are jointly significant in this equation.


| Variable name | Description   |
| ------------- |:-----------------------:|
| read          | Average reading score |
| math          | Average math score      |
| english       | Percent of English learners      |
| students      | Total enrollment      |
| teachers      | Number of teachers   |
| expenditure   | Expenditure per student   |


<hr />

<!--..........................................................................-->
### *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.7.1 <- lm(score ~ str + english + expenditure, data = CASchools)

# install required package if necessary 
# install.packages("car")

# load required package
library("car")

# Test for joint significance
linearHypothesis(lm.7.1,c("str=0","expenditure=0"))
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.7.1 <- lm(score ~ str + english + expenditure, data = CASchools)

# install required package if necessary 
# install.packages("car")

# load required package
library("car")

# Test for joint significance
linearHypothesis(lm.7.1,c("str=0","expenditure=0"))
```

<!--..........................................................................-->
### STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for Inference
use http://fmwww.bc.edu/ec-p/data/stockwatson/caschool.dta

# rename variables
rename testscr score
rename el_pct english
rename expn_stu expenditure
 
# calculate and store regression results
quietly reg score str english expenditure
 
# Test for joint significance
test expenditure str
```

<p class="head02">
Output 
</p>


<pre>

 ( 1)  expenditure = 0
 ( 2)  str = 0

       F(  2,   416) =    8.01
            Prob > F =    0.0004

</pre>


<!--..........................................................................-->
### Gretl {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Data
</p>

You can download and install the data sets from the Stock and Watson textbook from the following link: 
http://gretl.sourceforge.net/gretl_data.html \
The data sets are automatically saved in the Gretl folder under data. Alternatively, another storage location can be selected. Afterwards the data sets can easily be opened via the script with the command open. Alternatively, under the tab file, Open data can be selected and from the folder in which the data sets were stored the desired data set can be selected.

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
open caschool.gdt

# rename variables
rename el_pct english
rename testscr score
rename expn_stu expenditure

# calculate and store regression results
ols score 0 str english expenditure --quiet

# Test for joint significance
omit expenditure str --test-only
```

<p class="head02">
Output 
</p>


<pre>

  Null hypothesis: the regression parameters are zero for the variables
    expenditure, str
  Test statistic: F(2, 416) = 8.01013, p-value 0.000385975

</pre>



<!--..........................................................................-->
<!--..........................................................................-->

<!-- ## References -->

<!-- <hr /> -->

<!-- <p class="head01"> -->
<!-- References -->
<!-- </p> -->

<!--..........................................................................-->
## 
<!--..........................................................................-->

<!--..........................................................................-->
<hr />

<p class="back01">
[Back To *Start Software Implementation*](../index.html)
</p>

<!--..........................................................................-->
<hr />





<!--..........................................................................--> 
<!-- THIS IS THE END --> 

<!-- Include bottom -->

````{=html}
```{r, include=TRUE, echo=FALSE, results='asis'}
xfun::file_string('bottom_01.html')
```
````