---
title: "Introductory Econometrics"
subtitle: "*R* and *STATA* Code"
author: by Markus Mößler and Marc Bachmeier
output:
  html_document:
    highlight: tango
    css: style.css
    includes:
      in_header: logo.html
bibliography: [Teaching_References.bib]
biblio-style: apalike
link-citations: yes
nocite: | 
  @StockWatson2020Introduction
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Cross-Sectional Data | Inference {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 7.3
</p>

The dataset contains data on test performance, school characteristics and student demographic backgrounds for school districts in California with 420 observations on 14 variables. We calculate a linear regression with the average math and reading score as the dependent variable. We want to test if the student teacher ratio and the expenditure are jointly significant in this equation.


| Variable name | Description   |
| ------------- |:-----------------------:|
| read          | Average reading score |
| math          | Average math score      |
| english       | Percent of English learners      |
| students      | Total enrollment      |
| teachers      | Number of teachers   |
| expenditure   | Expenditure per student   |


<hr />

<!--..........................................................................-->
## *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.7.1 <- lm(score ~ str + english + expenditure, data = CASchools)

# install required package if necessary 
# install.packages("car")

# load required package
library("car")

# Test for joint significance
linearHypothesis(lm.7.1,c("str=0","expenditure=0"))
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.7.1 <- lm(score ~ str + english + expenditure, data = CASchools)

# install required package if necessary 
# install.packages("car")

# load required package
library("car")

# Test for joint significance
linearHypothesis(lm.7.1,c("str=0","expenditure=0"))
```

<!--..........................................................................-->
## STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for Inference
use http://fmwww.bc.edu/ec-p/data/stockwatson/caschool.dta

# rename variables
rename testscr score
rename el_pct english
rename expn_stu expenditure
 
# calculate and store regression results
quietly reg score str english expenditure
 
# Test for joint significance
test expenditure str
```

<p class="head02">
Output 
</p>


<pre>

 ( 1)  expenditure = 0
 ( 2)  str = 0

       F(  2,   416) =    8.01
            Prob > F =    0.0004

</pre>


<!--..........................................................................-->
<!--..........................................................................-->

## References

<hr />

<p class="head01">
References
</p>

<!--##########################################################################-->
<!-- THIS IS THE END --> 
<script>
var coll = document.getElementsByClassName("collapsible01");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>

<script>
var coll = document.getElementsByClassName("collapsible02");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>