---
title: "Introductory Econometrics"
subtitle: "*R* and *STATA* Code"
author: by Markus Mößler and Marc Bachmeier
output:
  html_document:
    highlight: tango
    css: style.css
    includes:
      in_header: logo.html
bibliography: [Teaching_References.bib]
biblio-style: apalike
link-citations: yes
nocite: | 
  @StockWatson2020Introduction
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Panel-Data | Fixed and random effects {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 10.3 
</p>

US traffic fatalities panel data for the “lower 48” US states (i.e., excluding Alaska and Hawaii), annually for 1982 through 1988 containing 336 observations on 34 variables. We calculate a linear regression with the fatality rate as the dependent variable and use different panel data methods such as pooled OLS, fixed effects and random effects. 

| Variable name | Description   |
| ------------- |:-----------------------:|
| fatal         | numeric. Number of vehicle fatalities |
| pop           | numeric. Population     |
| beertax       | numeric. Tax on case of beer     |
| year          | factor indicating year  |

<hr />

<!--..........................................................................-->
## *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->

<!--..........................................................................-->
### Pooled OLS {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# calculate and store regression results with pooled OLS
lm.1 <- lm(fatal_rate ~ beertax, data =  Fatalities)

# summarize regression results
summary(lm.1)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# calculate and store regression results with pooled OLS
lm.1 <- lm(fatal_rate ~ beertax, data =  Fatalities)

# summarize regression results
summary(lm.1)
```


<!--..........................................................................-->
### Fixed Effects {.tabset .tabset-fade}
<!--..........................................................................-->

<!--..........................................................................-->
#### Approach 1 {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Estimation 
</p>

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# install required packages if necessary
#install.packages("plm")

# load required packages 
library ("plm")

# calculate and store regression results with fixed effects
plm.fe <- plm(fatal_rate ~ beertax, data = Fatalities, index = c("state", "year"), model = "within")

# summarize regression results
summary(plm.fe)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# install required packages if necessary
#install.packages("plm")

# load required packages 
library ("plm")

# calculate and store regression results with fixed effects
plm.fe <- plm(fatal_rate ~ beertax, data = Fatalities, index = c("state", "year"), model = "within")

# summarize regression results
summary(plm.fe)

```

<hr />

<p class="head01">
Robust inference 
</p>

<hr />


<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# install required packages if necessary
#install.packages("plm")
#install.packages("lmtest")
#install.packages("sandwich")

# load required packages 
library ("plm")
library ("lmtest")
library ("sandwich")

# calculate and store regression results with fixed effects
plm.fe <- plm(fatal_rate ~ beertax, data = Fatalities, index = c("state", "year"), model = "within")

# calculate Heteroskedasticity-Robust Variance.Covariance matrix
HC.10.3 <- vcovHC(plm.fe, type = "HC1")

# Robust inference
coeftest(plm.fe, vcov=HC.10.3)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# install required packages if necessary
#install.packages("plm")
#install.packages("lmtest")
#install.packages("sandwich")

# load required packages 
library ("plm")
library ("lmtest")
library ("sandwich")

# calculate and store regression results with fixed effects
plm.fe <- plm(fatal_rate ~ beertax, data = Fatalities, index = c("state", "year"), model = "within")

# calculate Heteroskedasticity-Robust Variance.Covariance matrix
HC.10.3 <- vcovHC(plm.fe, type = "HC1")

# Robust inference
coeftest(plm.fe, vcov=HC.10.3)
```


<!--..........................................................................-->
#### Approach 2 {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# calculate and store regression results for OLS regression with dummies for every individual
lm.2 <- lm(fatal_rate ~ beertax + factor(state), data = Fatalities)

# summarize regression results
summary(lm.2)
```


<hr />


<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# calculate and store regression results for OLS regression with dummies for every individual
lm.2 <- lm(fatal_rate ~ beertax + factor(state), data = Fatalities)

# summarize regression results
summary(lm.2)
```

<hr />


<!--..........................................................................-->
#### Approach 3 {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# install required packages if necessary
#install.packages("plm")

# load required packages 
library ("plm")

# calculate and store regression results with fixed effects
plm.fe <- plm(fatal_rate ~ beertax, data = Fatalities, index = c("state", "year"), model = "within")

# Extract individual fixed effects
fixef(plm.fe,type="dmean")
```


<hr />


<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# install required packages if necessary
#install.packages("plm")

# load required packages 
library ("plm")

# calculate and store regression results with fixed effects
plm.fe <- plm(fatal_rate ~ beertax, data = Fatalities, index = c("state", "year"), model = "within")

# Extract individual fixed effects
fixef(plm.fe,type="dmean")
```


<!--..........................................................................-->
### Random Effects {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# install required packages if necessary
#install.packages("plm")

# load required packages 
library ("plm")

# calculate and store regression results with random effects
plm.re <- plm(fatal_rate ~ beertax, data = Fatalities, index = c("state", "year"), model = "random")

# summarize regression results
summary(plm.re)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("Fatalities")

# generate new variables for regression
Fatalities$fatal_rate <- Fatalities$fatal / Fatalities$pop * 10000

# install required packages if necessary
#install.packages("plm")

# load required packages 
library ("plm")

# calculate and store regression results with random effects
plm.re <- plm(fatal_rate ~ beertax, data = Fatalities, index = c("state", "year"), model = "random")

# summarize regression results
summary(plm.re)
```

<!--..........................................................................-->
## STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<!--..........................................................................-->
### Pooled OLS {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/fatality.dta
 
# Panel identifier
iis state

# Time identifier
tis year

# generate new variables for regression
gen fatal_rate= allmort/pop*10000 

# calculate and show regression results with pooled OLS
reg fatal_rate beertax
```

<hr />

<p class="head02">
Output 
</p>


<pre>

      Source |       SS           df       MS      Number of obs   =       336
-------------+----------------------------------   F(1, 334)       =     34.39
       Model |  10.1686591         1  10.1686591   Prob > F        =    0.0000
    Residual |  98.7468534       334  .295649262   R-squared       =    0.0934
-------------+----------------------------------   Adj R-squared   =    0.0906
       Total |  108.915513       335  .325120933   Root MSE        =    .54374

------------------------------------------------------------------------------
  fatal_rate |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
     beertax |   .3646054   .0621698     5.86   0.000     .2423117    .4868992
       _cons |   1.853308   .0435671    42.54   0.000     1.767607    1.939008
------------------------------------------------------------------------------

</pre>


<!--..........................................................................-->
### Fixed Effects {.tabset .tabset-fade}
<!--..........................................................................-->

<!--..........................................................................-->
#### Approach 1 {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Estimation 
</p>

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/fatality.dta
 
# Panel identifier
iis state

# Time identifier
tis year

# generate new variables for regression
gen fatal_rate= allmort/pop*10000 

# Calculate and show regression results with fixed effects
xtreg fatal_rate beertax, fe 
```

<hr />

<p class="head02">
Output 
</p>


<pre>

Fixed-effects (within) regression               Number of obs     =        336
Group variable: state                           Number of groups  =         48

R-sq:                                           Obs per group:
     within  = 0.0407                                         min =          7
     between = 0.1101                                         avg =        7.0
     overall = 0.0934                                         max =          7

                                                F(1,287)          =      12.19
corr(u_i, Xb)  = -0.6885                        Prob > F          =     0.0006

------------------------------------------------------------------------------
  fatal_rate |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
     beertax |  -.6558737     .18785    -3.49   0.001    -1.025612   -.2861353
       _cons |   2.377075   .0969699    24.51   0.000     2.186213    2.567937
-------------+----------------------------------------------------------------
     sigma_u |  .71471463
     sigma_e |  .18985942
         rho |  .93408484   (fraction of variance due to u_i)
------------------------------------------------------------------------------
F test that all u_i=0: F(47, 287) = 52.18                    Prob > F = 0.0000

</pre>

<hr />

<p class="head01">
Robust inference 
</p>

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/fatality.dta
 
# Panel identifier
iis state

# Time identifier
tis year

# generate new variables for regression
gen fatal_rate= allmort/pop*10000 

# Calculate and show regression results with fixed effects and robust standard errors
xtreg fatal_rate beertax, fe vce(cluster state)
```

<hr />

<p class="head02">
Output 
</p>


<pre>

Fixed-effects (within) regression               Number of obs     =        336
Group variable: state                           Number of groups  =         48

R-sq:                                           Obs per group:
     within  = 0.0407                                         min =          7
     between = 0.1101                                         avg =        7.0
     overall = 0.0934                                         max =          7

                                                F(1,47)           =       5.05
corr(u_i, Xb)  = -0.6885                        Prob > F          =     0.0294

                                 (Std. Err. adjusted for 48 clusters in state)
------------------------------------------------------------------------------
             |               Robust
  fatal_rate |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
     beertax |  -.6558737   .2918557    -2.25   0.029    -1.243012   -.0687359
       _cons |   2.377075   .1497967    15.87   0.000     2.075723    2.678427
-------------+----------------------------------------------------------------
     sigma_u |  .71471463
     sigma_e |  .18985942
         rho |  .93408484   (fraction of variance due to u_i)
------------------------------------------------------------------------------

</pre>


<!--..........................................................................-->
#### Approach 2 {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/fatality.dta
 
# Panel identifier
iis state

# Time identifier
tis year

# generate new variables for regression
gen fatal_rate= allmort/pop*10000 

# calculate and show regression results for OLS regression with dummies for every individual
reg fatal_rate beertax i.state
```

<hr />

<p class="head02">
Output 
</p>


<pre>

      Source |       SS           df       MS      Number of obs   =       336
-------------+----------------------------------   F(48, 287)      =     56.97
       Model |  98.5701385        48  2.05354455   Prob > F        =    0.0000
    Residual |   10.345374       287  .036046599   R-squared       =    0.9050
-------------+----------------------------------   Adj R-squared   =    0.8891
       Total |  108.915513       335  .325120933   Root MSE        =    .18986

------------------------------------------------------------------------------
  fatal_rate |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
     beertax |  -.6558737     .18785    -3.49   0.001    -1.025612   -.2861353
             |
       state |
         AZ  |  -.5677269   .2666662    -2.13   0.034    -1.092596   -.0428574
         AR  |  -.6549516   .2190203    -2.99   0.003    -1.086041   -.2238617
         CA  |  -1.509469   .3043508    -4.96   0.000    -2.108512    -.910426
         CO  |   -1.48428   .2873532    -5.17   0.000    -2.049867   -.9186934
         CT  |  -1.862257   .2805333    -6.64   0.000    -2.414421   -1.310094
         DE  |  -1.307602   .2939478    -4.45   0.000    -1.886169   -.7290351
         FL  |  -.2681302   .1393267    -1.92   0.055     -.542362    .0061016
         GA  |    .524603   .1839474     2.85   0.005     .1625458    .8866601
         ID  |  -.6690224   .2579674    -2.59   0.010     -1.17677   -.1612745
         IL  |  -1.961623    .291496    -6.73   0.000    -2.535364   -1.387881
         IN  |  -1.461542   .2725398    -5.36   0.000    -1.997972   -.9251112
         IA  |  -1.543932   .2534422    -6.09   0.000    -2.042773   -1.045091
         KS  |  -1.223216   .2454374    -4.98   0.000    -1.706302   -.7401303
         KY  |  -1.217517   .2871651    -4.24   0.000    -1.782734   -.6523002
         LA  |  -.8471162   .1886685    -4.49   0.000    -1.218466   -.4757668
         ME  |  -1.107947   .1911213    -5.80   0.000    -1.484125   -.7317701
         MD  |   -1.70644   .2832189    -6.03   0.000    -2.263889    -1.14899
         MA  |  -2.109746   .2760991    -7.64   0.000    -2.653182    -1.56631
         MI  |  -1.484527    .236019    -6.29   0.000    -1.949074   -1.019979
         MN  |  -1.897213   .2650851    -7.16   0.000    -2.418971   -1.375456
         MS  |  -.0290798   .1484539    -0.20   0.845    -.3212763    .2631167
         MO  |  -1.296262    .266689    -4.86   0.000    -1.821176   -.7713473
         MT  |  -.3603915   .2639632    -1.37   0.173    -.8799409    .1591579
         NE  |  -1.522178   .2492797    -6.11   0.000    -2.012826    -1.03153
         NV  |  -.6007749   .2859531    -2.10   0.037    -1.163606   -.0379436
         NH  |  -1.254454   .2096847    -5.98   0.000    -1.667169   -.8417395
         NJ  |   -2.10575    .307196    -6.85   0.000    -2.710392   -1.501107
         NM  |    .426375   .2543206     1.68   0.095    -.0741952    .9269452
         NY  |   -2.18667   .2989041    -7.32   0.000    -2.774992   -1.598348
         NC  |   -.290465    .119841    -2.42   0.016    -.5263437   -.0545863
         ND  |  -1.623439   .2538142    -6.40   0.000    -2.123013   -1.123866
         OH  |  -1.674419   .2538142    -6.60   0.000    -2.173993   -1.174846
         OK  |   -.545061   .1691229    -3.22   0.001    -.8779396   -.2121823
         OR  |     -1.168   .2857154    -4.09   0.000    -1.730363   -.6056365
         PA  |  -1.767466   .2760991    -6.40   0.000    -2.310902    -1.22403
         RI  |  -2.265054   .2937591    -7.71   0.000     -2.84325   -1.686859
         SC  |   .5571737   .1099958     5.07   0.000      .340673    .7736744
         SD  |  -1.003721   .2096176    -4.79   0.000    -1.416304   -.5911381
         TN  |  -.8756586   .2680169    -3.27   0.001    -1.403187   -.3481306
         TX  |  -.9174734   .2455582    -3.74   0.000    -1.400797     -.43415
         UT  |   -1.16395   .1964178    -5.93   0.000    -1.550552   -.7773484
         VT  |  -.9660438    .211129    -4.58   0.000    -1.381601   -.5504862
         VA  |  -1.290183   .2041564    -6.32   0.000    -1.692017   -.8883496
         WA  |  -1.659524   .2834645    -5.85   0.000    -2.217457   -1.101591
         WV  |  -.8967541    .246611    -3.64   0.000     -1.38215   -.4113585
         WI  |  -1.759266   .2939478    -5.98   0.000    -2.337833   -1.180699
         WY  |  -.2285037   .3128959    -0.73   0.466    -.8443655    .3873581
             |
       _cons |    3.47763   .3133568    11.10   0.000     2.860861    4.094399
------------------------------------------------------------------------------

</pre>


<!--..........................................................................-->
#### Approach 3 {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/fatality.dta
 
# Panel identifier
iis state

# Time identifier
tis year

# generate new variables for regression
gen fatal_rate= allmort/pop*10000 

# Calculate regression results with fixed effects
quietly xtreg fatal_rate beertax, fe

# Extract individual fixed effects
predict individual_effect, u

# Tabulate inidivdual fixed effects
tabstat individual_effect, by(state)
```

<hr />

<p class="head02">
Output 
</p>


<pre>
Summary for variables: individual_effect
     by categories of: nr 

 state |      mean
-------+----------
    AL |  1.100555
    AZ |  .5328283
    AR |  .4456036
    CA | -.4089136
    CO | -.3837252
    CT | -.7617021
    DE | -.2070468
    FL |   .832425
    GA |  1.625158
    ID |  .4315327
    IL | -.8610674
    IN | -.3609864
    IA |  -.443377
    KS | -.1226608
    KY | -.1169618
    LA |   .253439
    ME | -.0073922
    MD | -.6058845
    MA | -1.009191
    MI | -.3839717
    MN | -.7966579
    MS |  1.071475
    MO | -.1957065
    MT |  .7401637
    NE | -.4216227
    NV |  .4997803
    NH | -.1538992
    NJ | -1.005194
    NM |   1.52693
    NY | -1.086115
    NC |  .8100902
    ND | -.5228841
    OH | -.5738641
    OK |  .5554942
    OR | -.0674447
    PA | -.6669111
    RI | -1.164499
    SC |  1.657729
    SD |  .0968344
    TN |  .2248966
    TX |  .1830818
    UT | -.0633952
    VT |  .1345114
    VA |  -.189628
    WA | -.5589685
    WV |  .2038011
    WI | -.6587111
    WY |  .8720515
-------+----------
 Total |  2.18e-09
------------------

</pre>

<!--..........................................................................-->
### Random Effects {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/fatality.dta
 
# Panel identifier
iis state

# Time identifier
tis year

# generate new variables for regression
gen fatal_rate= allmort/pop*10000 
 
# Calculate and show regression results with random effects
xtreg fatal_rate beertax, re
```

<p class="head02">
Output 
</p>


<pre>

Random-effects GLS regression                   Number of obs     =        336
Group variable: state                           Number of groups  =         48

R-sq:                                           Obs per group:
     within  = 0.0407                                         min =          7
     between = 0.1101                                         avg =        7.0
     overall = 0.0934                                         max =          7

                                                Wald chi2(1)      =       0.18
corr(u_i, X)   = 0 (assumed)                    Prob > chi2       =     0.6753

------------------------------------------------------------------------------
  fatal_rate |      Coef.   Std. Err.      z    P>|z|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
     beertax |  -.0520158   .1241758    -0.42   0.675    -.2953959    .1913643
       _cons |   2.067141   .0999715    20.68   0.000     1.871201    2.263082
-------------+----------------------------------------------------------------
     sigma_u |   .5157915
     sigma_e |  .18985942
         rho |  .88067496   (fraction of variance due to u_i)
------------------------------------------------------------------------------

</pre>

<!--..........................................................................-->
<!--..........................................................................-->

## References

<hr />

<p class="head01">
References
</p>

<!--##########################################################################-->
<!-- THIS IS THE END --> 
<script>
var coll = document.getElementsByClassName("collapsible01");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>

<script>
var coll = document.getElementsByClassName("collapsible02");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>