---
output:
  html_document:
    css: !expr c("./assets/style.css")
    includes:
      in_header: !expr c("./assets/header_01.html")
bibliography: [./assets/Ma_EconometricMethods_Literature.bib]
biblio-style: apalike
link-citations: no
editor_options: 
  chunk_output_type: console
---

<!--..........................................................................-->
<!--..........................................................................-->

````{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('./assets/header_02.html')
```
````

<!--..........................................................................-->
<hr />

# What is <span class="R">R</span>?

<div style="margin-left: 0pt">

<span class="R">R</span> is a powerful programming language and software for *statistical computing and graphics*.

* <span class="R">R</span> is freely available under the "GNU General Public License".
* <span class="R">R</span> project homepage: [https://www.r-project.org/](https://www.r-project.org/).

According to @PaarschGolyaev2016Gentle, <span class="R">R</span> is the "lingua franca" among statisticians.

An introduction into <span class="R">R</span> can be found in, e.g.,  @Kabacoff2015R or @VenablesSmith2020Introduction.

</div>



<!--..........................................................................-->
<hr />

# What is <span class="R">RStudio</span>?

<div style="margin-left: 0pt">

<span class="R">R</span> has no (native) *GUI* (Graphical User Interface) or *IDE* (Integrated Development Environment).

Instead, *GUIs/IDEs* are provided by third-party software. One of the most popular and free of charge *GUI/IDE* for <span class="R">R</span> is <span class="R">RStudio</span>.

<span class="R">RStudio</span> is a front-end application for developing <span class="R">R</span> code, and freely available under the "GNU Affero General Public License".

<span class="R">RStudio</span> is not necessary but it makes it easier to use <span class="R">R</span>. Thus, we recommend to use <span class="R">RStudio</span>.

<!-- However, <span class="R">RStudio</span> is based on <span class="R">R</span> so you have to install <span class="R">R</span> first (see below)! -->

</div>



<!--..........................................................................-->
<hr />

# Installation of <span class="R">R</span> and <span class="R">RStudio</span>

<!--..........................................................................-->
<!-- <hr /> -->

<p class="head01">
Step 1: Installation of <span class="R">R</span>
</p>

<!-- <span class="R">R</span> is a programming language and software for statistical computing and graphics and freely available under the "GNU General Public License". -->

<!--..........................................................................-->
<!-- <p class="head02"> -->
<!-- Steps -->
<!-- </p> -->

1. Go to [CRAN Mirrors](https://cran.r-project.org/mirrors.html)
2. Choose a mirror located close to your internet connection, e.g., "GWDG Göttingen".
3. Download and install <span class="R">R</span> for your operating system, e.g., "Windows".

<!--..........................................................................-->
<!-- <hr /> -->

<p class="head01">
Step 2: Installation of <span class="R">RStudio</span>
</p>

<!-- <span class="R">RStudio</span> is a so-called "integrated development environment" (IDE), i.e., a front-end application for developing R code, and freely available under the "GNU Affero General Public License". -->

<!-- <span class="R">RStudio</span> is not necessary to use <span class="R">R</span> but it makes it easier. Thus, we recommend to use <span class="R">RStudio</span>. However, <span class="R">RStudio</span> is based on <span class="R">R</span> so you have to install <span class="R">R</span> first (see above)! -->

<!--..........................................................................-->
<!-- <p class="head02"> -->
<!-- Steps -->
<!-- </p> -->

1. Go to [download <span class="R">RStudio</span>](https://posit.co/download/rstudio-desktop/)
2. Choose "<span class="R">RStudio</span> Desktop".
3. Download and install <span class="R">RStudio</span> for your operating system, e.g., "Windows".

*Note, <span class="R">RStudio</span> is based on <span class="R">R</span> so you have to install <span class="R">R</span> first (see above)!*


<!--..........................................................................-->
<hr />

# Literature

<div id="refs"></div>

<!--..........................................................................-->
<hr />

<p class="back01">
[Back To *Start* of *Practical Class*](./index.html)
</p>

<!--..........................................................................-->
<hr />





<!--..........................................................................--> 
<!-- THIS IS THE END --> 

<!-- Include bottom -->

````{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('./assets/bottom_01.html')
```
````