---
output:
  html_document:
    css: !expr c("./assets/style.css")
    includes:
      in_header: !expr c("./assets/header_01.html")
params:
  dat_link_01: "https://ilias.uni-hohenheim.de/goto.php?target=file_1523858_download&client_id=UHOH"
  dat_nam_01: "CASchools_01_data.txt"
editor_options: 
  chunk_output_type: console
---

<!--..........................................................................-->
<!--..........................................................................-->

<!-- Include header -->

````{=html}
```{r, include=TRUE, echo=FALSE, results='asis'}
xfun::file_string('./assets/header_02.html')
```
````

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}

knitr::opts_chunk$set(
  include=FALSE,
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center')
# See: https://stackoverflow.com/questions/36230790/missing-horizontal-scroll-bar-in-r-markdown-html-code-chunks-and-output
options(width=1000)

```

```{r}

# # 1) clear workspace # exclude to be able to use params in yml header!
# rm(list=ls(all=TRUE))

# 2) load libraries
library(kableExtra)

# 3) load r-scripts
source("./r-scripts/texreg_extract_fun.R")
source("./r-scripts/r_helper_functions.R")

# 4) load data
cas.dat <- read.table(file = "./data-sets/CASchools_01_data.txt",
                      header = TRUE,
                      sep = ",",
                      colClasses = c("numeric","numeric","numeric","numeric"))

```

```{r,klippy, echo=FALSE, include=TRUE}

# See: https://rlesur.github.io/klippy/articles/klippy.html
klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))

```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Exercise Sheet No 02 {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Linear Regression with One Regressor (Part 1)
</p>

We want to analyze the relationship between student performance and class size. For this we use again the data set `CASchool_01_data.txt` and the two variables $test score$ and $STR$ as obtained in the first exercise sheet.

<hr />

<p class="head02">
Variables
</p>

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Show Variable Description* </button>
<div class="col_content">

| Variable   | Description            | 
|:-----------|:-----------------------| 
| $students$ | Total enrollment.      | 
| $teachers$ | Number of teachers.    | 
| $read$     | Average reading score. | 
| $math$     | Average math score.    | 

</div>
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
## Set-Up

<span style="text-decoration: none; font-size: 18pt">
1)
</span>
<span style="text-decoration: underline; font-size: 18pt">
Create your (working) directory
</span>

Create a new folder on your computer in which you can save all necessary files, i.e., the data set, the <span class="R">R</span> *script* with the implementation of your analysis and the <span class="R">R</span> *helper function script* with some helper functions provided by us.

This folder, i.e., the path or directory of this folder, will be your so-called working directory.

<hr />

<span style="text-decoration: none; font-size: 18pt">
2)
</span>
<span style="text-decoration: underline; font-size: 18pt">
Download the data set
</span>

<!-- Download the data sets `CASchools_01_data` from <span class="R">ILIAS</span> directly or by using the link below: -->

<!-- <p class="down01"> -->
<!-- <a href="https://ilias.uni-hohenheim.de/goto.php?target=file_1523858_download&client_id=UHOH">Download `CASchools_01_data.txt`</a> -->
<!-- </p> -->

Download the data sets ``r params$dat_nam_01`` from <span class="R">ILIAS</span> or by using the link below:

<p class="down01">
<a href="`r params$dat_link_01`">Download ``r params$dat_nam_01``</a>
</p>

Save the data set into your (working) directory.

<hr />

<span style="text-decoration: none; font-size: 18pt">
3)
</span>
<span style="text-decoration: underline; font-size: 18pt">
Prepare *script*
</span>

Open a new <span class="R">R</span> *script* and save it into into your (working) directory.

Run the following code chunk to prepare your <span class="R">R</span> *script*, i.e., to clear the work space and set your working directory.

```{r,include=TRUE,echo=TRUE,eval=FALSE}

# Clear workspace
rm(list = ls(all = TRUE))
# Set working directory
setwd(".../set/your/working/directory/...")

```

<hr />

<div style="display:none">

<span style="text-decoration: none; font-size: 18pt">
X)
</span>
<span style="text-decoration: underline; font-size: 18pt">
Install *libraries*
</span>

Run the following code chunk to make sure that all necessary *libraries* are installed.

*Note*, You have to run this code chunk only once. After running this code chunk you have installed all necessary *libraries* for the class and we will load them whenever we need them.

```{r,include=TRUE,echo=TRUE,eval=FALSE,include=FALSE}

# packages we will use in the course
pac <- c("moments", "sandwich", "lmtest", "AER", "car", "plm", "ivreg", "dynlm", "forecast", "urca")

# install and/or load packages
checkpac <- function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x)
  }
  require(x, character.only = TRUE)
}

# check if packages are install yet
suppressWarnings(sapply(pac, checkpac))

```

<hr />

</div>

<span style="text-decoration: none; font-size: 18pt">
4)
</span>
<span style="text-decoration: underline; font-size: 18pt">
Install/load *packages* and download/save/include *helper function script*
</span>

<span style="text-decoration: underline">Step 1</span>) Install all relevant <span class="R">R</span> *packages* and download and save the <span class="R">R</span> *script* `r_helper_functions.R` from <span class="R">ILIAS</span> by running the following code chunk.

```{r,include=TRUE,echo=TRUE,eval=FALSE}

# Download R-helper functions
source("https://ilias.uni-hohenheim.de/data/UHOH/lm_data/lm_1856939/MA_EconometricMethods_WiSe2324_PracticalClass/r-scripts/prepare_r_packages_and_helper_functions.R")

```

*Note*, the required <span class="R">R</span> *packages* are `"moments"`, `"sandwich"`, `"lmtest"`, `"lmtest"`, `"car"`, `"plm"`, `"ivreg"`, `"dynlm"`, `"forecast"`, `"urca"`.

<div style="margin-top: 5px;">
<span style="text-decoration: underline">Step 2</span>) Include the <span class="R">R</span> *script* `r_helper_functions.R` into your <span class="R">R</span> *script* by running the following code chunk.
</div>

```{r,include=TRUE,echo=TRUE,eval=FALSE}

# Include R-helper functions
source("r_helper_functions.R")

```

*Note*, more information on the helper functions can be found [here](./00_ExerciseSheet_HelperFunctions_XX.html).





<!--..........................................................................-->
## Data/Variables

Load data and construct variables.

<hr />

<p class="head02">
Load data set
</p>

<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Code* </button>
<div class="cod_content">
```{r,include=TRUE,echo=TRUE,results=FALSE,eval=FALSE}
# load the data set
cas.dat <- read.table(file = "CASchools_01_data.txt",
                      header = TRUE,
                      sep = ",",
                      colClasses = c("numeric","numeric","numeric","numeric"))
```
</div>
<!--..........................................................................-->

<hr />

<p class="head02">
Construct variables
</p>

<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Code* </button>
<div class="cod_content">
```{r,include=TRUE,echo=TRUE,results=FALSE}
# compute STR and append it to cas.dat
cas.dat$STR <- cas.dat$students/cas.dat$teachers 
# compute TestScore and append it to cas.dat
cas.dat$score <- (cas.dat$read + cas.dat$math)/2 
```
</div>
<!--..........................................................................-->

<hr />





<!--..........................................................................-->
## Task a) 

Specify the population regression model using $score$ as dependent variable and $STR$ as independent variable. Estimate the intercept and the slope parameter. Interpret the results depicted in Table 1 on the exercise sheet.

<hr />

<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Code* </button>
<div class="cod_content">
```{r,include=TRUE,echo=TRUE,results=FALSE}
# estimate the model and assign the result to lin.mod
lin.mod <- lm(score ~ STR, data = cas.dat)
# show results
lin.mod
```
</div>
<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Output* </button>
<div class="cod_content">
```{r,include=TRUE,echo=FALSE,results=TRUE}
# estimate the model and assign the result to lin.mod
lin.mod <- lm(score ~ STR, data = cas.dat)
# show results
lin.mod
```
</div>
<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Output (after some additional transformations!)* </button>
<div class="cod_content">
```{r,include=TRUE,echo=FALSE,results=TRUE}
# estimate the model and assign the result to lin.mod
lin.mod <- lm(score ~ STR, data = cas.dat)
```

```{r,include=TRUE}
screenreg(lin.mod,
       caption = "Estimation Results",
       caption.above = TRUE,
       label = "Tab03",
       stars = numeric(0),
       custom.model.names = NULL,
       custom.coef.names = c("intercept","STR"),
       float.pos = "h",
       single.row = TRUE,
       booktabs = TRUE,
       dcolumn = TRUE,
       use.packages = FALSE,
       ci.force = FALSE,
       digits = 2,
       include.rsquared = TRUE,
       include.adjrs = FALSE,
       include.nobs = FALSE,
       include.rmse = TRUE,
       doctype = FALSE)
```
</div>
<!--..........................................................................-->

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Note* </button>
<div class="col_content">

Use the function `lm()` to fit a linear model.

The resulting object, i.e., here, `lin.mod` is of class `lm` and contains various information about the model fitting.

```{r,include=FALSE,echo=FALSE}
# informations in lin.mod
str(lin.mod)
```

E.g., you can extract coefficients estimates, residuals and fitted values.

```{r,include=TRUE,echo=TRUE}
# coefficients
lin.mod$coefficients
# residuals
head(lin.mod$residuals)
# fitted values
head(lin.mod$fitted.values)
```

The most important information can be extracted using the general `summary()` function.

```{r,include=TRUE,echo=TRUE}
# summary
summary(lin.mod)
```

</div>
<!--..........................................................................-->

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Interpretation: Regression Model Specification* </button>
<div class="col_content">

<div style="color: red" class="showSol01">

<!-- <hr /> -->

<p class="head02">
Regression model
</p>

\begin{align*}
Y_i &= \beta_0 + \beta_1 X_i + u_i \\
score &= \beta_0 + \beta_1 STR + \text{error}
\end{align*}

<hr />

<p class="head02">
Population regression line/function
</p>

\begin{align*}
Y_i &= \beta_0 + \beta_1 X_i \\
score &= \beta_0 + \beta_1 STR
\end{align*}

<!-- <hr /> -->

</div>

<div style="color: red" class="noSol01">

*Add the population regression model here!*

</div>

</div>
<!--..........................................................................-->

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Interpretation: OLS Estimator* </button>
<div class="col_content">

<div style="color: red" class="showSol01">

<!-- <hr /> -->

<p class="head02">
Ordinary Least Squares (OLS) estimator
</p>

\begin{align*}
min_{\beta_0,\beta_1} \sum^n_{i = 1} \left[Y_i - \left(\beta_0 + \beta_1 X_i\right)\right]^2
\end{align*}

$\Rightarrow$ The Result of this minimization is the OLS estimator for $\beta_0$ and $\beta_1$, denoted $\hat{\beta}_0$ and $\hat{\beta}_1$.

<hr />

<p class="head02">
Sample regression line/function
</p>

\begin{align*}
\widehat{score} &= \hat{\beta}_0 + \hat{\beta}_1  STR \\
\widehat{score} &= `r round(lin.mod$coefficients[c("(Intercept)")],2)` + \left(`r round(lin.mod$coefficients[c("STR")],2)`\right)  STR \\
\end{align*}

<!-- <hr /> -->

</div>

<div style="color: red" class="noSol01">

*Add your interpretation here!*

</div>

</div>
<!--..........................................................................-->

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Interpretation: Results* </button>
<div class="col_content">

<div style="color: red" class="showSol01">

<!-- <hr /> -->

<!-- <p class="head02"> -->
<!-- In general $\underline{\left(\Delta STR=1\right)}$ -->
<!-- </p> -->

<span style="text-decoration:underline; font-size:18pt;">In general</span> $\left(\Delta STR=1\right)$:

* $\hat{\beta}_0$: No reasonable interpretation here.
* $\hat{\beta}_1$: Increase/difference of the class size by one student, i.e., $\Delta STR=1$, relates to a change/difference in score of on average `r round(lin.mod$coefficients[c("STR")],2)` points.

<hr />

<!-- <p class="head02"> -->
<!-- In particular $\underline{\left(\Delta STR=2\right)}$ -->
<!-- </p> -->

<span style="text-decoration:underline; font-size:18pt;">In particular</span> $\left(\Delta STR=2\right)$:

* $\Delta STR=2$: Increase from 50th percentile to almost 90th percentile ($\Rightarrow$ large change!)
* $\Delta score=`r 2*round(lin.mod$coefficients[c("STR")],2)`$: Decrease from 50th percentile to almost 40th percentile ($\Rightarrow$ small change!)

<!-- <hr /> -->

<span style="text-decoration:underline; font-size:18pt;">Remember</span>:

```{r, include=FALSE}

# compute sample averages of STR and score
avg.str <- mean(cas.dat$STR) 
avg.sco <- mean(cas.dat$score)
# compute sample standard deviations of STR and score
sd.str <- sd(cas.dat$STR) 
sd.sco <- sd(cas.dat$score)
# set up a vector of percentiles and compute the percentiles 
per <- c(0.10, 0.25, 0.4, 0.5, 0.6, 0.75, 0.9)
per.str <- quantile(cas.dat$STR, per)
per.sco <- quantile(cas.dat$score, per)
# gather everything in a data.frame 
dis.sum.02 <- data.frame(avg = c(avg.str, avg.sco), 
                         sd = c(sd.str, sd.sco), 
                         per = rbind(per.str, per.sco))

cas.dat.sum.tab.02 <- format(round(cbind(dis.sum.02),2),2)
colnames(cas.dat.sum.tab.02) <- c("Average","SD","10%","25%","40%","50%","60%","75%","90%")
rownames(cas.dat.sum.tab.02) <- c("STR","score")

```

```{r,include=TRUE,results='asis'}
cas.dat.sum.tab.02 %>%
  kable("html",booktabs=T,escape=F,align="r") %>%
  add_header_above(c(" ", " " = 2, "Percentile" = 7)) %>%
  kable_styling(latex_options="hold_position") %>%
  row_spec(0,align="c")
```

</div>

<div style="color: red" class="noSol01">

*Add your interpretation here!*

</div>

</div>
<!--..........................................................................-->





## Task b)

Based on the estimation results depicted in Table 1 of the exercise sheet calculate the predicted value and the residual for the district Del Paso Heights, Sacramento, CA, for which $STR=20.81$ and $score=612.65$.

<hr />

<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Code* </button>
<div class="cod_content">
```{r,include=TRUE,echo=TRUE,results=FALSE}
# index of Del Paso Heights (dph), Sacramento, CA
ii.dph <- which(round(cas.dat$STR, 2) == 20.81)
# score of Del Paso Heights (dph), Sacramento, CA
sco.dph <- cas.dat$score[ii.dph] # (=612.65)
# predicted score for Del Paso Heights
pre.dph <- 698.93-2.28*20.81
pre.dph
# residual value
res.dph <- sco.dph - pre.dph
res.dph
```
</div>
<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Output (with some additional notes!)* </button>
<div class="cod_content">
```{r,include=TRUE,echo=FALSE,results=TRUE}
# index of Del Paso Heights (dph), Sacramento, CA
ii.dph <- which(round(cas.dat$STR, 2) == 20.81)
# score of Del Paso Heights (dph), Sacramento, CA
sco.dph <- cas.dat$score[ii.dph] # (=612.65)
# predicted score for Del Paso Heights
pre.dph <- 698.93-2.28*20.81
paste("predicted sore: ", round(pre.dph, 2), sep = "")
# residual value
res.dph <- sco.dph-pre.dph
paste("residual value: ", round(res.dph, 2), sep = "")
```
</div>
<!--..........................................................................-->

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Note* </button>
<div class="col_content">

Use the function `which()` to get the index which fulfills a certain condition, here, rounded $STR$ equals $20.81$.

</div>
<!--..........................................................................-->

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Interpretation* </button>
<div class="col_content">

<div style="color: red" class="showSol01">

* Prediction of $score$ for "Del Paso Heights, Sacramento, CA": `r round(pre.dph,2)`
    * ($\Rightarrow$ in-sample prediction)
* Residual value for "Del Paso Heights, Sacramento, CA": `r round(res.dph,2)`

</div>

<div style="color: red" class="noSol01">

*Add your interpretation here!*

</div>

</div>
<!--..........................................................................-->





## Task c)

<hr />

Evaluate the fit of the regression line based on the information depicted in Table 1 of the exercise sheet. Explain the concept of the two measures and interpret the results.

<!-- Regression $R^2$ -->

<hr />

<p class="head02">
Regression $\underline{R^2}$
</p>

<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Code* </button>
<div class="cod_content">
```{r,include=TRUE,echo=TRUE,results=FALSE}
# calculate explained sum of squares (ESS)
ess <- sum((fitted(lin.mod) - mean(cas.dat$score))^2)
ess
# calculate total sum of squares (TSS)
tss <- sum((cas.dat$score - mean(cas.dat$score))^2)
tss
# compare TSS with (n-1) times variance of score
tss.chk <- (length(cas.dat$score) - 1)*var(cas.dat$score)
tss.chk
# compute R2
r2 <- ess/tss
r2
# or use sum of squared residuals (SSR)
ssr <- sum(residuals(lin.mod)^2)
ssr
# compute R2
r2.chk <- 1 - ssr/tss
r2.chk
```
</div>
<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Output (with some additional notes!)* </button>
<div class="cod_content">
```{r,include=TRUE,echo=FALSE,results=TRUE}
# calculate explained sum of squares (ESS)
ess <- sum((fitted(lin.mod) - mean(cas.dat$score))^2)
paste("ESS: ", round(ess,2), sep="")
# calculate total sum of squares (TSS)
tss <- sum((cas.dat$score - mean(cas.dat$score))^2)
paste("TSS: ", round(tss,2), sep="")
# compare TSS with (n-1) times variance of score
tss.chk <- (length(cas.dat$score)-1)*var(cas.dat$score)
paste("TSS (check): ", round(tss.chk,2), sep="")
# compute R2
r2 <- ess/tss
paste("R2: ", round(r2,2), sep="")
# or use sum of squared residuals (SSR)
ssr <- sum(residuals(lin.mod)^2)
paste("SSR: ", round(ssr,2), sep="")
# compute R2
r2 <- 1- ssr/tss
paste("R2 (check): ", round(r2,2), sep="")
```
</div>
<!--..........................................................................-->





<!--..........................................................................-->
<button type="button" class="collapsible02"> *Interpretation: $R^2$* </button>
<div class="col_content">

<div style="color: red" class="showSol01">

<p class="head02">
Remember
</p>

\begin{align}
  ESS & =  \sum_{i = 1}^n \left( \widehat{Y_i} - \overline{Y} \right)^2,   \\
  TSS & =  \sum_{i = 1}^n \left( Y_i - \overline{Y} \right)^2,   \\
  R^2 & = \frac{ESS}{TSS}.
\end{align}

<p class="head02">
Here
</p>

* Fraction of the sample variance of $Y$ (i.e., $score$) explained by (or predicted) by $X$ (i.e., $STR$).
* `r round(r2,2)*100` percent of the sample variance of $score$ can be explained/predicted by $STR$.

</div>

<div style="color: red" class="noSol01">

*Add your interpretation here!*

</div>

</div>
<!--..........................................................................-->

<!-- Standard Error of the Regression $SER$ -->

<hr />

<p class="head02">
Standard Error of the Regression $\underline{SER}$
</p>

<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Code* </button>
<div class="cod_content">
```{r,include=TRUE,echo=TRUE,results=FALSE}
# calculate sum of squared residuals (SSR) (see above)
ssr <- sum(residuals(lin.mod)^2)
ssr
# calculate standard error of the regression (SER)
nn <- length(cas.dat$score) # number of observations
ser <- sqrt(1/(nn-2)*ssr)
ser
```
</div>
<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Output (with some additional notes!)* </button>
<div class="cod_content">
```{r,include=TRUE,echo=FALSE,results=TRUE}
# calculate sum of squared residuals (SSR) (see above)
ssr <- sum(residuals(lin.mod)^2)
paste("SSR: ", round(ssr,2), sep="")
# calculate standard error of the regression (SER)
nn <- length(cas.dat$score) # number of observations
ser <- sqrt(1/(nn-2)*ssr)
paste("SER: ", round(ser,2), sep="")
```
</div>
<!--..........................................................................-->

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Interpretation: $SER$* </button>
<div class="col_content">

<div style="color: red" class="showSol01">

<p class="head02">
Remember
</p>

$$ SER = s_{\widehat{u}} = \sqrt{s_{\widehat{u}}^2} \ \ \ \text{where} \ \ \ s_{\widehat{u} }^2 = \frac{1}{n-2} \sum_{i = 1}^n \hat{u}^2_i = \frac{SSR}{n - 2} $$

<p class="head02">
Here
</p>

* Estimator of the standard deviation of the regression error $u_i$. Note, $u_i$ is not observable.
* Measure of the spread of the observations around the regression line in units of the dependent variable (i.e. $score$).
* $\Rightarrow$ Rather large spread of the observations around the regression line.

</div>

<div style="color: red" class="noSol01">

*Add your interpretation here!*

</div>

</div>
<!--..........................................................................-->





## Else

<p class="head02">
Scatter Plot with Fitted Regression Line (revisited)
</p>

<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Code* </button>
<div class="cod_content">
```{r,include=TRUE,echo=TRUE,results=FALSE,fig.show='hide'}
# plot parameters
par(mfrow=c(1, 1),
    mar=c(5, 5, 3, 2))
# scatterplot
plot(cas.dat$STR, cas.dat$score,
     main = "Scatter Plot of Test Score and STR", 
     xlab = "STR (X)",
     ylab = "Test Score (Y)")
abline(lin.mod, col = "red", lty = 2)
```
</div>
<!--..........................................................................-->
<button type="button" class="collapsible01"> *Show Output* </button>
<div class="cod_content">
```{r,include=TRUE,echo=FALSE,results=TRUE}
# plot parameters
par(mfrow=c(1, 1),
    mar=c(5, 5, 3, 2))
# scatterplot
plot(cas.dat$STR, cas.dat$score,
     main = "Scatter Plot of Test Score and STR", 
     xlab = "STR (X)",
     ylab = "Test Score (Y)")
abline(lin.mod, col = "red", lty = 2)
```
</div>
<!--..........................................................................-->

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Note* </button>
<div class="col_content">

The function `abline()` with an `lm` object as argument  (here: `lin.mod`) extracts...

* first the estimated coefficients of the `lm` object and...
* second, plots a line based on the estimated coefficients.

</div>
<!--..........................................................................-->

<!--..........................................................................-->
<button type="button" class="collapsible02"> *Some additional insights* </button>
<div class="col_content">

<p class="head03">
Scatter Plot with Fitted Regression Line (again)
</p>

```{r,include=TRUE,echo=FALSE,results=TRUE}
# fitted values score head
cas.dat$score.h <- fitted(lin.mod)
TT <- nrow(cas.dat)
# plot parameters
par(mfrow=c(1, 1),
    mar=c(5, 5, 3, 2))
# scatterplot
plot(cas.dat$STR, cas.dat$score,
     main = "Scatter Plot of Test Score, Fitted Test Score and STR", 
     xlab = "STR (X)",
     ylab = "Test Score (Y)",
     col = "blue")
lines(cas.dat$STR, cas.dat$score.h,
      type = "p",
      col = "red")
abline(h = mean(cas.dat$score),
       col = "black",
       lty = 2)
# deviations of fitted scores from the mean
for (ii in 1:TT) {
  lines(c(cas.dat$STR[ii], cas.dat$STR[ii]), c(mean(cas.dat$score), cas.dat$score.h[ii]),
      type = "l",
      col = "red",
      lty = 3)
}
# deviations of observed scores from the mean
for (ii in 1:TT) {
  lines(c(cas.dat$STR[ii], cas.dat$STR[ii]), c(mean(cas.dat$score), cas.dat$score[ii]),
      type = "l",
      col = "blue",
      lty = 3)
}
```

<p class="head03">
Explanation
</p>

<div style="margin-left: 10pt">

<u>Dots</u>:

* Blue: Observed values $score_i$
* Red: Fitted values $\widehat{score}_i$

<u>Horizontal dashed line</u>:

* Mean of the observed values $\overline{score}$

<u>Vertical dashed lines</u>:

* Blue: Deviations of the observed values from the mean $\left(score_i - \overline{score}\right)$
* Red: Deviations of the fitted values from the mean $\left(\widehat{score}_i - \overline{score}\right)$

<u>Interpretation</u>:

* Explained sum of squares (*ESS*) or explained variation of $score_i$ based on the regression model are the square (*red*) deviations.
* Total sum of squares (*TSS*) or total variation of $score_i$ are the squared (*blue*) deviations.
* Here, (only) 5% of *TSS* (*blue* squared) can be captured by the model (*red* squared).

</div>

</div>
<!--..........................................................................-->





<!-- <hr /> -->

<!-- ## Literature -->

<!-- <p class="head01"> -->
<!-- Literature -->
<!-- </p> -->

<!-- <div id="refs"></div> -->

<!--..........................................................................-->
# 
<!--..........................................................................-->

<!--..........................................................................-->
<hr />

<p class="back01">
[Back To *Start* of *Practical Class*](./index.html)
</p>

<!--..........................................................................-->
<hr />

```{r}

library(class)
train <- rbind(iris3[1:25,,1], iris3[1:25,,2], iris3[1:25,,3])
test <- rbind(iris3[26:50,,1], iris3[26:50,,2], iris3[26:50,,3])
cl <- factor(c(rep("s",25), rep("c",25), rep("v",25)))
knn.k3 <- knn(train, test, cl, k = 3, prob=TRUE)
attributes(.Last.value)

```

```{r}

score.fac <- as.factor(cas.dat$score)
score.fac

knn.res <- knn(train = cbind(cas.dat$STR), test = cbind(cas.dat$STR), cl = score.fac, k = 1, prob = TRUE)

attributes(.Last.value)

```

```{r}

ord.id <- order(cas.dat$STR)

head(sort(cas.dat$STR))
head(cas.dat$STR[ord.id])



NN <- length(cas.dat$score)

ord.id <- order(cas.dat$score)

k <- 2
xk <- vector(mode = "list")
xk[[1]] <- cas.dat$STR[ord.id][1:k]

for (ii in 2:round(NN/k)) {
  
  ii.seq <- seq(1, NN, k)
  
  ii.seq[ii] + k - 1
  
  xk[[ii]] <- cas.dat$STR[ord.id][ii.seq[ii]:(ii.seq[ii] + k - 1)]
  
}

xxx <- sapply(xk, mean)

length(xxx)

xxx[1]

xk[[1]]

mean(c(21.40625, 19.50000))



x <- cas.dat$STR
y <- cas.dat$score
k <- 2





NN <- length(y)
ord.id <- order(y)

yk <- vector(mode = "list")

# collapse to mean across k successive values
yk[[1]] <- y[ord.id][1:k]
for (ii in 2:round(NN/k)) {
  ii.seq <- seq(1, NN, k)
  ii.seq[ii] + k - 1
  yk[[ii]] <- y[ord.id][ii.seq[ii]:(ii.seq[ii] + k - 1)]
}
y.k.means <- sapply(yk, mean)

# expand for plot
y.k.fit <- cbind(y.k.means) %x% rbind(1,1)

plot(x[ord.id], y.k.fit,
     col = "blue",
     ylim = c(600, 720))
lines(cas.dat$STR, cas.dat$score,
      type = "p",
      col = "red")
grid()

plot(x[ord.id], y.k.fit,
     col = "blue",
     ylim = c(600, 720))
lines(cas.dat$STR, cas.dat$score,
      type = "p",
      col = "red")
grid()


plot(seq(1, NN), y.k.fit,
     col = "black",
     ylim = c(600, 720))
lines(seq(1, TT), y[ord.id],
      type = "l",
      col = "darkgreen")
lines(seq(1, TT), cas.dat$score.h[order(cas.dat$score.h)],
      type = "l",
      col = "red")
grid()


```










<!--..........................................................................--> 
<!-- THIS IS THE END --> 

<!-- Include bottom -->

````{=html}
```{r, include=TRUE, echo=FALSE, results='asis'}
xfun::file_string('./assets/bottom_01.html')
```
````

````{=html}

<script>

// Hide all solutions (by default)
var i, Sol01;
Sol01 = document.getElementsByClassName("showSol01");
for (i = 0; i < Sol01.length; i++) {
  Sol01[i].style.display = "none"; // type "block" for show or "none" (default) for exclude
}
  
var i, NoSol01;
NoSol01 = document.getElementsByClassName("noSol01");
for (i = 0; i < NoSol01.length; i++) {
  NoSol01[i].style.display = "block"; // type "block" (default) for show or "none" for exclude
}

</script>

````
