---
output:
  html_document:
    css: !expr c("./assets/style.css")
    includes:
      in_header: !expr c("./assets/header_01.html")
bibliography: [./assets/Ma_EconometricMethods_Literature.bib]
biblio-style: apalike
link-citations: no
nocite: | 
  @StockWatson2020Introduction
params:
  ilias_course_link: "https://ilias.uni-hohenheim.de/goto.php?target=crs_1513853&client_id=UHOH" # change!
  illustration_link_01: "https://ilias.uni-hohenheim.de/data/UHOH/lm_data/lm_1776644/illustration-statistical-concepts/sim-hyp-tes-ill/sim_hyp_tes_ill.html" # fixed!
editor_options: 
  chunk_output_type: console
---

<!--..........................................................................-->
<!--..........................................................................-->

<!-- Include header -->

````{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('./assets/header_02.html')
```
````

```{r,klippy, echo=FALSE, include=TRUE}

# See: https://rlesur.github.io/klippy/articles/klippy.html
# remotes::install_github("rlesur/klippy")
klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))

```

<!--..........................................................................-->
<!--..........................................................................-->

<!--..........................................................................-->
<hr />

# Approach

<div style="margin-left: 20pt">

This *Learning Module* contains the implementation of the empirical analysis of the *Exercise Sheets* of the course *Econometric Methods in Business and Economics* in <span class="R">R</span>.

Use the *links* below to get to the implementation of the respective *Exercise Sheet*.

Note, for each new *Exercise Sheet* another *link* will be added. Thus, the content of the *Learning Module* will expand during the semester.

Further details will be provided in the *Practical Class*.

</div>



<!--..........................................................................-->
<hr />

# Installation of and short Introduction to <span class="R">R</span>

<div style="margin-left: 20pt">

This link contains information on the [installation of <span class="R">R</span>](./00_RInstallation_XX.html).

This link contains a very short [introduction to <span class="R">R</span>](./00_RBasics_XX.html). 

</div>



<!--..........................................................................-->
<hr />

# Exercise Sheets

<div style="margin-left: 10pt">

<table style="width:100%">
  <tr>
    <th style="width:4%"></th>
    <th style="width:25%"></th>
    <th style="width:59%"></th>
    <th style="width:12%"></th>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>1)</span>
    </td>
    <td>
    Exercise Sheet No 01:
    </td>
    <td>
    California Test Score Data Set
    </td>
    <td>
    &#10140; [Link](01_ExerciseSheet_No01_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>2)</span>
    </td>
    <td>
    Exercise Sheet No 02:
    </td>
    <td>
    Linear Regression with One Regressor (Part 1)
    </td>
    <td>
    &#10140; [Link](02_ExerciseSheet_No02_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>3)</span>
    </td>
    <td>
    Exercise Sheet No 03:
    </td>
    <td>
    Linear Regression with One Regressor (Part 2)
    </td>
    <td>
    &#10140; [Link](03_ExerciseSheet_No03_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>4)</span>
    </td>
    <td>
    Exercise Sheet No 04:
    </td>
    <td>
    Linear Regression with One Regressor (Part 3)
    </td>
    <td>
    &#10140; [Link](04_ExerciseSheet_No04_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>5)</span>
    </td>
    <td>
    Exercise Sheet No 05:
    </td>
    <td>
    Linear Regression with Multiple Regressors (Part 1)
    </td>
    <td>
    &#10140; [Link](05_ExerciseSheet_No05_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>6)</span>
    </td>
    <td>
    Exercise Sheet No 06:
    </td>
    <td>
    Linear Regression with Multiple Regressors (Part 2)
    </td>
    <td>
    &#10140; [Link](06_ExerciseSheet_No06_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>7)</span>
    </td>
    <td>
    Exercise Sheet No 07:
    </td>
    <td>
    Linear Regression with Multiple Regressors (Part 3)
    </td>
    <td>
    &#10140; [Link](07_ExerciseSheet_No07_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>8)</span>
    </td>
    <td>
    Exercise Sheet No 08:
    </td>
    <td>
    Regression Analysis with Panel Data
    </td>
    <td>
    &#10140; [Link](08_ExerciseSheet_No08_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>9)</span>
    </td>
    <td>
    Exercise Sheet No 09:
    </td>
    <td>
    Regression Analysis with a Binary Dependent Variable
    </td>
    <td>
    &#10140; [Link](09_ExerciseSheet_No09_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>10)</span>
    </td>
    <td>
    Exercise Sheet No 10:
    </td>
    <td>
    Instrumental Variable Regression (Mock Exam Part II)
    </td>
    <td>
    &#10140; [Link](10_ExerciseSheet_No10_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>11)</span>
    </td>
    <td>
    Exercise Sheet No 11:
    </td>
    <td>
    Regression Analysis of Time Series Data (Part 1)
    </td>
    <td>
    &#10140; [Link](11_ExerciseSheet_No11_XX.html)
    </td>
  </tr>
  <!-- ..... -->
  <tr style="border: 2px solid tomato">
    <td style="text-align:center">
    <span>12)</span>
    </td>
    <td>
    Exercise Sheet No 12:
    </td>
    <td>
    Regression Analysis of Time Series Data (Part 2)
    </td>
    <td>
    &#10140; [Link](12_ExerciseSheet_No12_XX.html)
    </td>
  </tr>
  
</table>

<!-- <p style="text-indent: 20pt">...</p> -->

<table style="width:100%">
  <tr>
    <th style="width:4%"></th>
    <th style="width:25%"></th>
    <th style="width:59%"></th>
    <th style="width:12%"></th>
  </tr>
  <!-- ..... -->
  <tr>
    <td style="text-align:center">
    <span>X)</span>
    </td>
    <td>
    Mock Exam Part I:
    </td>
    <td>
    Linear Regression with Multiple Regressors
    </td>
    <td>
    &#10140; [Link](XX_MockExam_TaskNo01_XX.html)
    </td>
  </tr>

</table>

</div>

<!--..........................................................................-->
<hr />

# Facultative Assignment

Please find a solution of the facultative assignment [here](./XX_Assignment_XX.html).

Note, this is a very extensive solution and is only partly representative for the evaluation of the solutions handed in.

<!--..........................................................................-->
<hr />

# Implementation in other statistic software packages

<div style="margin-left: 20pt">

A comparison of the implementation of basic econometric methods in <span class="emp01">R</span>, <span class="emp01">STATA</span> and <span class="emp01">gretl</span> can be found here:

</div>

<center>
<span class="emp01">[Implementation in other statistic software packages](./software-implementations/index.html)</span></span>

<span class="emp01">Note, additional support is only provided for <span class="R">R!</span></span>
</center>

<!-- .......................................................................... -->
<hr />

# Illustrations

<div style="margin-left: 20pt">
[Illustration of hypothesis test](`r params$illustration_link_01`)
</div>

<!--..........................................................................-->
<hr />

# Literature

<div style="margin-left: 20pt">

<div id="refs"></div>

</div>

<!--..........................................................................-->
<hr />

# Contributors

This learning module was developed by:

* Domenic Franjic (as reasearch assistant and PhD student)
* Markus Mößler (as reasearch assistant and PhD student)
* Damilola Aladesuru (as student assistant)
* Marc Bachmeier (as student assistant)

<!--..........................................................................-->
<hr />

<p class="back01">
[Back To *ILIAS*](`r params$ilias_course_link`)
</p>

<!--..........................................................................-->
<hr />

<!--..........................................................................--> 
<!-- THIS IS THE END --> 

<!-- Include bottom -->

````{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('./assets/bottom_01.html')
```
````
