---
title: "Introductory Econometrics"
subtitle: "*R* and *STATA* Code"
author: by Markus Mößler and Marc Bachmeier
output:
  html_document:
    highlight: tango
    css: style.css
    includes:
      in_header: logo.html
bibliography: [Teaching_References.bib]
biblio-style: apalike
link-citations: yes
nocite: | 
  @StockWatson2020Introduction
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Cross-Sectional Data | Heteroskedasticity {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 16.4
</p>

The dataset contains data on test performance, school characteristics and student demographic backgrounds for school districts in California with 420 observations on 14 variables. We calculate a linear regression with the average math and reading score as the dependent variable. We want to test if the student teacher ratio and the expenditure are jointly significant in this equation.


| Variable name | Description   |
| ------------- |:-----------------------:|
| read          | Average reading score |
| math          | Average math score      |
| english       | Percent of English learners      |
| students      | Total enrollment      |
| teachers      | Number of teachers   |
| expenditure   | Expenditure per student   |


<hr />

<!--..........................................................................-->
## *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.16.4 <- lm(score ~ str + english, data = CASchools)

# install required packages if necessary
#install.packages("lmtest")
#install.packages("sandwich")

# load required packages 
library ("lmtest")
library ("sandwich")

# calculate Heteroskedasticity-Robust Variance-Covariance matrix
HC.16.4 <- vcovHC(lm.16.4, type = "HC1")

# Robust inference
coeftest(lm.16.4, vcov=HC.16.4)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.16.4 <- lm(score ~ str + english, data = CASchools)

# install required packages if necessary
#install.packages("lmtest")
#install.packages("sandwich")

# load required packages 
library ("lmtest")
library ("sandwich")

# calculate Heteroskedasticity-Robust Variance-Covariance matrix
HC.16.4 <- vcovHC(lm.16.4, type = "HC1")

# Robust inference
coeftest(lm.16.4, vcov=HC.16.4)
```

<!--..........................................................................-->
## STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/caschool.dta
 
# rename variables
rename el_pct english
rename expn_stu expenditure
rename testscr score
 
# calculate and show regression results with Heteroskedasticity-Robust Standard Errors
reg score str english, robust
```

<p class="head02">
Output 
</p>


<pre>

Linear regression                               Number of obs     =        420
                                                F(2, 417)         =     223.82
                                                Prob > F          =     0.0000
                                                R-squared         =     0.4264
                                                Root MSE          =     14.464

------------------------------------------------------------------------------
             |               Robust
       score |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
         str |  -1.101296   .4328472    -2.54   0.011     -1.95213   -.2504616
     english |  -.6497768   .0310318   -20.94   0.000     -.710775   -.5887786
       _cons |   686.0322   8.728224    78.60   0.000     668.8754     703.189
------------------------------------------------------------------------------

</pre>


<!--..........................................................................-->
<!--..........................................................................-->

## References

<hr />

<p class="head01">
References
</p>

<!--##########################################################################-->
<!-- THIS IS THE END --> 
<script>
var coll = document.getElementsByClassName("collapsible01");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>

<script>
var coll = document.getElementsByClassName("collapsible02");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>