---
output: html_fragment
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Cross-Sectional Data
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
## Heteroskedasticity {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 16.4
</p>

The dataset contains data on test performance, school characteristics and student demographic backgrounds for school districts in California with 420 observations on 14 variables. We calculate a linear regression with the average math and reading score as the dependent variable. We want to test if the student teacher ratio and the expenditure are jointly significant in this equation.


| Variable name | Description   |
| ------------- |:-----------------------:|
| read          | Average reading score |
| math          | Average math score      |
| english       | Percent of English learners      |
| students      | Total enrollment      |
| teachers      | Number of teachers   |
| expenditure   | Expenditure per student   |


<hr />

<!--..........................................................................-->
### *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.16.4 <- lm(score ~ str + english, data = CASchools)

# install required packages if necessary
#install.packages("lmtest")
#install.packages("sandwich")

# load required packages 
library ("lmtest")
library ("sandwich")

# calculate Heteroskedasticity-Robust Variance-Covariance matrix
HC.16.4 <- vcovHC(lm.16.4, type = "HC1")

# Robust inference
coeftest(lm.16.4, vcov=HC.16.4)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.16.4 <- lm(score ~ str + english, data = CASchools)

# install required packages if necessary
#install.packages("lmtest")
#install.packages("sandwich")

# load required packages 
library ("lmtest")
library ("sandwich")

# calculate Heteroskedasticity-Robust Variance-Covariance matrix
HC.16.4 <- vcovHC(lm.16.4, type = "HC1")

# Robust inference
coeftest(lm.16.4, vcov=HC.16.4)
```

<!--..........................................................................-->
### STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/caschool.dta
 
# rename variables
rename el_pct english
rename expn_stu expenditure
rename testscr score
 
# calculate and show regression results with Heteroskedasticity-Robust Standard Errors
reg score str english, robust
```

<p class="head02">
Output 
</p>


<pre>

Linear regression                               Number of obs     =        420
                                                F(2, 417)         =     223.82
                                                Prob > F          =     0.0000
                                                R-squared         =     0.4264
                                                Root MSE          =     14.464

------------------------------------------------------------------------------
             |               Robust
       score |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
         str |  -1.101296   .4328472    -2.54   0.011     -1.95213   -.2504616
     english |  -.6497768   .0310318   -20.94   0.000     -.710775   -.5887786
       _cons |   686.0322   8.728224    78.60   0.000     668.8754     703.189
------------------------------------------------------------------------------

</pre>


<!--..........................................................................-->
### Gretl {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Data
</p>

You can download and install the data sets from the Stock and Watson textbook from the following link: 
http://gretl.sourceforge.net/gretl_data.html \
The data sets are automatically saved in the Gretl folder under data. Alternatively, another storage location can be selected. Afterwards the data sets can easily be opened via the script with the command open. Alternatively, under the tab file, Open data can be selected and from the folder in which the data sets were stored the desired data set can be selected.

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
open caschool.gdt

# rename variables
rename el_pct english
rename testscr score

# calculate and show regression results with Hteroskedasticity-Robust Standard Errors
ols score 0 str english --robust
```

<p class="head02">
Output 
</p>


<pre>

Model 1: OLS, using observations 1-420
Dependent variable: score
Heteroskedasticity-robust standard errors, variant HC1

             coefficient   std. error   t-ratio    p-value 
  ---------------------------------------------------------
  const      686.032       8.72822       78.60    3.98e-252 ***
  str         −1.10130     0.432847      −2.544   0.0113    **
  english     −0.649777    0.0310318    −20.94    4.70e-067 ***

Mean dependent var   654.1565   S.D. dependent var   19.05335
Sum squared resid    87245.29   S.E. of regression   14.46448
R-squared            0.426431   Adjusted R-squared   0.423680
F(2, 417)            223.8229   P-value(F)           9.28e-67
Log-likelihood      −1716.561   Akaike criterion     3439.123
Schwarz criterion    3451.243   Hannan-Quinn         3443.913

</pre>



<!--..........................................................................-->
<!--..........................................................................-->

<!-- ## References -->

<!-- <hr /> -->

<!-- <p class="head01"> -->
<!-- References -->
<!-- </p> -->

<!--..........................................................................-->
## 
<!--..........................................................................-->

<!--..........................................................................-->
<hr />

<p class="back01">
[Back To *Start Software Implementation*](../index.html)
</p>

<!--..........................................................................-->
<hr />





<!--..........................................................................--> 
<!-- THIS IS THE END --> 

<!-- Include bottom -->

````{=html}
```{r, include=TRUE, echo=FALSE, results='asis'}
xfun::file_string('bottom_01.html')
```
````