---
output: html_fragment
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,include=FALSE}
library("devtools")
# devtools::install_github("ijlyttle/vembedr")
library("vembedr")
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Using GRETL IDE
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
## Introduction {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
### GRETL UI {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
GRETL User Interface
</p>

This section provides an overview of the GRETL user interface by describing the basic function of the different icons, tools and options available for use upon loading the GRETL application.
<br>
</br>

```{r, include=TRUE,echo=FALSE}
embed_url("https://youtu.be/uckghBijdxI") %>%
    use_align("center")  %>%
    use_bs_responsive()
```


<!--..........................................................................-->
### Loading Data {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Loading Data in GRETL 
</p>

How to access available dataset from different econometrics textbooks on the GRETL server and how to use dataset available in the computer's user library.
<br>
</br>

```{r, include=TRUE,echo=FALSE}
embed_url("https://youtu.be/LwPzK_yQBTw") %>%
    use_align("center")  %>%
    use_bs_responsive()
```


<!--..........................................................................-->
### Data Structure {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Setting Data Structure 
</p>

When using data from a local file, GRETL always requires that the structure of the dataset be specified i.e. to indicate whether the dataset is cross-sectional, time-series or a panel data. For data downloaded from the GRETL server, this and additonal information about the dataset is already loaded into GRETL.
<br>
</br>

```{r, include=TRUE,echo=FALSE}
embed_url("https://youtu.be/YaHSg-DsqGw") %>%
    use_align("center")  %>%
    use_bs_responsive()
```


<!--..........................................................................-->
#
<!--..........................................................................-->


<!--..........................................................................-->
<!--..........................................................................-->

<!-- ## References -->

<!-- <hr /> -->

<!-- <p class="head01"> -->
<!-- References -->
<!-- </p> -->

<!--..........................................................................-->
## 
<!--..........................................................................-->

<!--..........................................................................-->
<hr />

<p class="back01">
[Back To *Start Software Implementation*](../../index.html)
</p>

<!--..........................................................................-->
<hr />





<!--..........................................................................--> 
<!-- THIS IS THE END --> 

<!-- Include bottom -->

````{=html}
```{r, include=TRUE, echo=FALSE, results='asis'}
xfun::file_string('bottom_01.html')
```
````