---
output: html_fragment
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,include=FALSE}
library("devtools")
# devtools::install_github("ijlyttle/vembedr")
library("vembedr")
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Using GRETL IDE
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
## Introduction {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
### Log file {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
How to Generate Log Files in GRETL 
</p>

Generating a log file is crucial for saving scripts or lines of code which are used to complete an econometric estimation. This allows for easy review and revision of work done.
<br>
</br>
More specifically, log files will be required along other exercise submissions in this module thus, it is important to learn how to generate them when using the GRETL GUI.
<br>
</br>

```{r, include=TRUE,echo=FALSE}
embed_url("https://youtu.be/LwPzK_yQBTw") %>%
    use_align("center")  %>%
    use_bs_responsive()
```



<!--..........................................................................-->
### Session Icon View {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Session Icon View
</p>

The session icon view tab in GRETL allows user to save graphs, tables and econometrics models for outputs to be printed, saved as pdf, word or processed LaTex.
<br>
</br>
Learn some of the things that can be done with the tab and then, independently explore more possibilities.

<br>
</br>

<p class="head02">
Saving results using session icon view 'Graph page'
</p>

```{r, include=TRUE,echo=FALSE}
embed_url("https://youtu.be/5jZhMlnWmFY") %>%
    use_align("center")  %>%
    use_bs_responsive()
```


<br>
</br>

<p class="head02">
Saving outputs using session icon view 'Model table'
</p>

```{r, include=TRUE,echo=FALSE}
embed_url("https://youtu.be/5jZhMlnWmFY") %>%
    use_align("center")  %>%
    use_bs_responsive()
```



<!--..........................................................................-->
#
<!--..........................................................................-->


<!--..........................................................................-->
<!--..........................................................................-->

<!-- ## References -->

<!-- <hr /> -->

<!-- <p class="head01"> -->
<!-- References -->
<!-- </p> -->

<!--..........................................................................-->
## 
<!--..........................................................................-->

<!--..........................................................................-->
<hr />

<p class="back01">
[Back To *Start Software Implementation*](../../index.html)
</p>

<!--..........................................................................-->
<hr />





<!--..........................................................................--> 
<!-- THIS IS THE END --> 

<!-- Include bottom -->

````{=html}
```{r, include=TRUE, echo=FALSE, results='asis'}
xfun::file_string('bottom_01.html')
```
````