---
title: "Introductory Econometrics"
subtitle: "*R* and *STATA* Code"
author: by Markus Mößler and Marc Bachmeier
output:
  html_document:
    highlight: tango
    css: style.css
    includes:
      in_header: logo.html
bibliography: [Teaching_References.bib]
biblio-style: apalike
link-citations: yes
nocite: | 
  @StockWatson2020Introduction
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Cross-Sectional Data | Limited Dependent Variable {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 11.4
</p>

Cross-section data on the Home Mortgage Disclosure Act contains 2380 observations on 14 variables. The dummy variable if the mortgage was denied is our dependent variable in a logit and a probit model.

| Variable name | Description   |
| ------------- |:-----------------------:|
| deny          | Factor. Was the mortgage denied? |
| afam          | Factor. Is the individual African-American?     |
| pirat         | Payments to income ratio  |
| hirat         | Housing expense to income ratio |
| lvrat         | Loan to value ratio  |
| chist         | Factor. Credit history: consumer payments  |
| mhist         | Factor. Credit history: mortgage payments    |
| phist         | Factor. Public bad credit record?   |
| insurance     | Factor. Was the individual denied mortgage insurance?   |
| selfemp       | Factor. Is the individual self-employed?    |

<hr />

<!--..........................................................................-->
## *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->


<!--..........................................................................-->
### Logit {.tabset .tabset-fade}
<!--..........................................................................-->


<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("HMDA")

#adjust variables for regression
HMDA$lvrat <- factor(
  ifelse(HMDA$lvrat < 0.8, "low",
  ifelse(HMDA$lvrat >= 0.8 & HMDA$lvrat <= 0.95, "medium", "high")),
  levels = c("low", "medium", "high"))
HMDA$mhist <- as.numeric(HMDA$mhist)
HMDA$chist <- as.numeric(HMDA$chist)


# calculate and store regression results with logit model
logit.11.4 <- glm(deny ~ afam + pirat + hirat + lvrat + chist + mhist + phist 
                  + insurance + selfemp, data = HMDA, family = binomial(link = "logit"))

# summarize regression results
summary(logit.11.4)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("HMDA")

#adjust variables for regression
HMDA$lvrat <- factor(
  ifelse(HMDA$lvrat < 0.8, "low",
  ifelse(HMDA$lvrat >= 0.8 & HMDA$lvrat <= 0.95, "medium", "high")),
  levels = c("low", "medium", "high"))
HMDA$mhist <- as.numeric(HMDA$mhist)
HMDA$chist <- as.numeric(HMDA$chist)

# calculate and store regression results with logit model
logit.11.4 <- glm(deny ~ afam + pirat + hirat + lvrat + chist + mhist + phist 
                  + insurance + selfemp, data = HMDA, family = binomial(link = "logit"))

# summarize regression results
summary(logit.11.4)
```

<!--..........................................................................-->
### Probit {.tabset .tabset-fade}
<!--..........................................................................-->


<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("HMDA")

# adjust variables for regression
HMDA$lvrat <- factor(
  ifelse(HMDA$lvrat < 0.8, "low",
  ifelse(HMDA$lvrat >= 0.8 & HMDA$lvrat <= 0.95, "medium", "high")),
  levels = c("low", "medium", "high"))
HMDA$mhist <- as.numeric(HMDA$mhist)
HMDA$chist <- as.numeric(HMDA$chist)

# calculate and store regression results with probit model
probit.11.4 <- glm(deny ~ afam + pirat + hirat + lvrat + chist + mhist + phist 
                  + insurance + selfemp, data = HMDA, family = binomial(link = "probit"))

# summarize regression results
#summary(probit.11.4)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("HMDA")

# adjust variables for regression
HMDA$lvrat <- factor(
  ifelse(HMDA$lvrat < 0.8, "low",
  ifelse(HMDA$lvrat >= 0.8 & HMDA$lvrat <= 0.95, "medium", "high")),
  levels = c("low", "medium", "high"))
HMDA$mhist <- as.numeric(HMDA$mhist)
HMDA$chist <- as.numeric(HMDA$chist)

# calculate and store regression results with probit model
probit.11.4 <- glm(deny ~ afam + pirat + hirat + lvrat + chist + mhist + phist 
                  + insurance + selfemp, data = HMDA, family = binomial(link = "probit"))

# summarize regression results
summary(probit.11.4)
```


<!--..........................................................................-->
## STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<!--..........................................................................-->
### Logit {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/hmda_sw.dta

# adjust variables for regression
gen afam= (s13==3)
gen mhist = s42
gen chist = s43
gen phist = (s44>0)
gen insurance = (s53==1)
gen selfemp = (s27a==1)
gen deny= (s7==3)
gen hirat= s45/100
gen pirat= s46/100
gen lvrat = s6/s50
gen lvratmedium = (lvrat>=0.80)*(lvrat<=0.95)
gen lvrathigh = (lvrat>0.95) 


# calculate and show regression results with logit model
logit deny afam pirat hirat lvratmedium lvrathigh chist mhist phist insurance selfemp
```

<p class="head02">
Output 
</p>


<pre>

Iteration 0:   log likelihood =  -872.0853  
Iteration 1:   log likelihood = -672.05096  
Iteration 2:   log likelihood = -656.94676  
Iteration 3:   log likelihood = -636.05789  
Iteration 4:   log likelihood = -635.63857  
Iteration 5:   log likelihood = -635.63667  
Iteration 6:   log likelihood = -635.63667  

Logistic regression                             Number of obs     =      2,380
                                                LR chi2(10)       =     472.90
                                                Prob > chi2       =     0.0000
Log likelihood = -635.63667                     Pseudo R2         =     0.2711

------------------------------------------------------------------------------
        deny |      Coef.   Std. Err.      z    P>|z|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
        afam |   .6884231   .1773918     3.88   0.000     .3407416    1.036105
       pirat |   4.764416   1.042587     4.57   0.000     2.720983     6.80785
       hirat |  -.1088114   1.239403    -0.09   0.930    -2.537996    2.320374
 lvratmedium |    .463525    .159096     2.91   0.004     .1517025    .7753475
   lvrathigh |   1.494764   .3112213     4.80   0.000     .8847812    2.104746
       chist |   .2903017   .0398178     7.29   0.000     .2122603    .3683431
       mhist |   .2790178   .1399192     1.99   0.046     .0047811    .5532544
       phist |   1.225797   .2054334     5.97   0.000     .8231547    1.628439
   insurance |   4.548166   .5524863     8.23   0.000     3.465312    5.631019
     selfemp |   .6661288   .2115319     3.15   0.002     .2515338    1.080724
       _cons |  -5.707384   .4097911   -13.93   0.000    -6.510559   -4.904208
------------------------------------------------------------------------------

</pre>

<!--..........................................................................-->
### Probit {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/hmda_sw.dta

# adjust variables for regression
gen afam= (s13==3)
gen mhist = s42
gen chist = s43
gen phist = (s44>0)
gen insurance = (s53==1)
gen selfemp = (s27a==1)
gen deny= (s7==3)
gen hirat= s45/100
gen pirat= s46/100
gen lvrat = s6/s50
gen lvratmedium = (lvrat>=0.80)*(lvrat<=0.95)
gen lvrathigh = (lvrat>0.95) 


# calculate and show regression results with logit model
probit deny afam pirat hirat lvratmedium lvrathigh chist mhist phist insurance selfemp
```

<p class="head02">
Output 
</p>


<pre>

Iteration 0:   log likelihood =  -872.0853  
Iteration 1:   log likelihood = -643.92086  
Iteration 2:   log likelihood = -636.87532  
Iteration 3:   log likelihood = -636.84706  
Iteration 4:   log likelihood = -636.84706  

Probit regression                               Number of obs     =      2,380
                                                LR chi2(10)       =     470.48
                                                Prob > chi2       =     0.0000
Log likelihood = -636.84706                     Pseudo R2         =     0.2697

------------------------------------------------------------------------------
        deny |      Coef.   Std. Err.      z    P>|z|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
        afam |   .3891261   .0966749     4.03   0.000     .1996468    .5786054
       pirat |   2.441787   .5279727     4.62   0.000     1.406979    3.476594
       hirat |  -.1846764   .6519372    -0.28   0.777     -1.46245    1.093097
 lvratmedium |   .2139677   .0819881     2.61   0.009      .053274    .3746614
   lvrathigh |   .7910831   .1744755     4.53   0.000     .4491174    1.133049
       chist |   .1546224   .0214869     7.20   0.000     .1125089     .196736
       mhist |   .1477082   .0735792     2.01   0.045     .0034956    .2919209
       phist |   .6974496   .1190143     5.86   0.000     .4641859    .9307134
   insurance |   2.556796   .2814955     9.08   0.000     2.005075    3.108517
     selfemp |   .3586252     .11169     3.21   0.001     .1397168    .5775336
       _cons |  -3.040568   .2014292   -15.09   0.000    -3.435362   -2.645774
------------------------------------------------------------------------------

</pre>


<!--..........................................................................-->
## Gretl {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Data
</p>

You can download and install the data sets from the Stock and Watson textbook from the following link: 
http://gretl.sourceforge.net/gretl_data.html \
The data sets are automatically saved in the Gretl folder under data. Alternatively, another storage location can be selected. Afterwards the data sets can easily be opened via the script with the command open. Alternatively, under the tab file, Open data can be selected and from the folder in which the data sets were stored the desired data set can be selected.

<!--..........................................................................-->
### Logit {.tabset .tabset-fade}
<!--..........................................................................-->

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
open boston_hmda.gdt

# adjust variables for regression
genr afam = (s13==3)
genr mhist = s42
genr chist = s43
genr phist = (s44>0)
genr insureance = (s53==1)
genr selfemp = (s27a==1)
genr deny = (s7==3)
genr hirat = s45/100
genr pirat = s46/100
genr lvrat = s6/s50
genr lvratmedium = (lvrat>=0.80)*(lvrat<=0.95)
genr lvrathigh = (lvrat>0.95)


# calculate and show regression results with logit model
logit deny 0 afam pirat hirat lvratmedium lvrathigh chist mhist phist insureance selfemp
```

<p class="head02">
Output 
</p>


<pre>

Model 1: Logit, using observations 1-2380
Dependent variable: deny
Standard errors based on Hessian

                coefficient   std. error       z          slope   
  ----------------------------------------------------------------
  const          −5.70738     0.409791     −13.93                 
  afam            0.688423    0.177392       3.881      0.0604745 
  pirat           4.76442     1.04259        4.570      0.338242  
  hirat          −0.108811    1.23940       −0.08779   −0.00772488
  lvratmedium     0.463525    0.159096       2.913      0.0347313 
  lvrathigh       1.49476     0.311221       4.803      0.187854  
  chist           0.290302    0.0398178      7.291      0.0206095 
  mhist           0.279018    0.139919       1.994      0.0198084 
  phist           1.22580     0.205433       5.967      0.135211  
  insureance      4.54817     0.552486       8.232      0.807109  
  selfemp         0.666129    0.211532       3.149      0.0589217 

Mean dependent var   0.119748   S.D. dependent var   0.324735
McFadden R-squared   0.271130   Adjusted R-squared   0.258517
Log-likelihood      −635.6367   Akaike criterion     1293.273
Schwarz criterion    1356.797   Hannan-Quinn         1316.393

Number of cases 'correctly predicted' = 2155 (90.5%)
f(beta'x) at mean of independent vars = 0.071
Likelihood ratio test: Chi-square(10) = 472.897 [0.0000]

           Predicted
               0      1
  Actual 0  2067     28
         1   197     88

Excluding the constant, p-value was highest for variable 23 (hirat)

</pre>


<!--..........................................................................-->
### Probit {.tabset .tabset-fade}
<!--..........................................................................-->

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
open boston_hmda.gdt

# adjust variables for regression
genr afam = (s13==3)
genr mhist = s42
genr chist = s43
genr phist = (s44>0)
genr insureance = (s53==1)
genr selfemp = (s27a==1)
genr deny = (s7==3)
genr hirat = s45/100
genr pirat = s46/100
genr lvrat = s6/s50
genr lvratmedium = (lvrat>=0.80)*(lvrat<=0.95)
genr lvrathigh = (lvrat>0.95)


# calculate and show regression results with probit model
probit deny 0 afam pirat hirat lvratmedium lvrathigh chist mhist phist insureance selfemp
```

<p class="head02">
Output 
</p>


<pre>

Model 1: Probit, using observations 1-2380
Dependent variable: deny
Standard errors based on Hessian

                coefficient   std. error      z         slope   
  --------------------------------------------------------------
  const          −3.04057     0.201429     −15.09               
  afam            0.389126    0.0966749      4.025     0.0710011
  pirat           2.44179     0.527973       4.625     0.369302 
  hirat          −0.184676    0.651937      −0.2833   −0.0279309
  lvratmedium     0.213968    0.0819881      2.610     0.0336387
  lvrathigh       0.791083    0.174475       4.534     0.187192 
  chist           0.154622    0.0214869      7.196     0.0233855
  mhist           0.147708    0.0735792      2.007     0.0223398
  phist           0.697450    0.119014       5.860     0.153286 
  insureance      2.55680     0.281495       9.083     0.792706 
  selfemp         0.358625    0.111690       3.211     0.0652745

Mean dependent var   0.119748   S.D. dependent var   0.324735
McFadden R-squared   0.269742   Adjusted R-squared   0.257129
Log-likelihood      −636.8471   Akaike criterion     1295.694
Schwarz criterion    1359.218   Hannan-Quinn         1318.814

Number of cases 'correctly predicted' = 2150 (90.3%)
f(beta'x) at mean of independent vars = 0.151
Likelihood ratio test: Chi-square(10) = 470.476 [0.0000]

           Predicted
               0      1
  Actual 0  2068     27
         1   203     82

Excluding the constant, p-value was highest for variable 23 (hirat)

Test for normality of residual -
  Null hypothesis: error is normally distributed
  Test statistic: Chi-square(2) = 5.78411
  with p-value = 0.0554622

</pre>


<!--..........................................................................-->
<!--..........................................................................-->

## References

<hr />

<p class="head01">
References
</p>

<!--##########################################################################-->
<!-- THIS IS THE END --> 
<script>
var coll = document.getElementsByClassName("collapsible01");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>

<script>
var coll = document.getElementsByClassName("collapsible02");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>