---
title: "Introductory Econometrics"
subtitle: "*R* and *STATA* Code"
author: by Markus Mößler and Marc Bachmeier
output:
  html_document:
    highlight: tango
    css: style.css
    includes:
      in_header: logo.html
bibliography: [Teaching_References.bib]
biblio-style: apalike
link-citations: yes
nocite: | 
  @StockWatson2020Introduction
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Cross-Sectional Data | Limited Dependent Variable {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 11.4
</p>

Cross-section data on the Home Mortgage Disclosure Act contains 2380 observations on 14 variables. The dummy variable if the mortgage was denied is our dependent variable in a logit and a probit model.

| Variable name | Description   |
| ------------- |:-----------------------:|
| deny          | Factor. Was the mortgage denied? |
| afam          | Factor. Is the individual African-American?     |
| pirat         | Payments to income ratio  |
| hirat         | Housing expense to income ratio |
| lvrat         | Loan to value ratio  |
| chist         | Factor. Credit history: consumer payments  |
| mhist         | Factor. Credit history: mortgage payments    |
| phist         | Factor. Public bad credit record?   |
| insurance     | Factor. Was the individual denied mortgage insurance?   |
| selfemp       | Factor. Is the individual self-employed?    |

<hr />

<!--..........................................................................-->
## *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->


<!--..........................................................................-->
### Logit {.tabset .tabset-fade}
<!--..........................................................................-->


<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("HMDA")

#adjust variables for regression
HMDA$lvrat <- factor(
  ifelse(HMDA$lvrat < 0.8, "low",
  ifelse(HMDA$lvrat >= 0.8 & HMDA$lvrat <= 0.95, "medium", "high")),
  levels = c("low", "medium", "high"))
HMDA$mhist <- as.numeric(HMDA$mhist)
HMDA$chist <- as.numeric(HMDA$chist)


# calculate and store regression results with logit model
logit.11.4 <- glm(deny ~ afam + pirat + hirat + lvrat + chist + mhist + phist 
                  + insurance + selfemp, data = HMDA, family = binomial(link = "logit"))

# summarize regression results
summary(logit.11.4)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("HMDA")

#adjust variables for regression
HMDA$lvrat <- factor(
  ifelse(HMDA$lvrat < 0.8, "low",
  ifelse(HMDA$lvrat >= 0.8 & HMDA$lvrat <= 0.95, "medium", "high")),
  levels = c("low", "medium", "high"))
HMDA$mhist <- as.numeric(HMDA$mhist)
HMDA$chist <- as.numeric(HMDA$chist)

# calculate and store regression results with logit model
logit.11.4 <- glm(deny ~ afam + pirat + hirat + lvrat + chist + mhist + phist 
                  + insurance + selfemp, data = HMDA, family = binomial(link = "logit"))

# summarize regression results
summary(logit.11.4)
```

<!--..........................................................................-->
### Probit {.tabset .tabset-fade}
<!--..........................................................................-->


<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("HMDA")

# adjust variables for regression
HMDA$lvrat <- factor(
  ifelse(HMDA$lvrat < 0.8, "low",
  ifelse(HMDA$lvrat >= 0.8 & HMDA$lvrat <= 0.95, "medium", "high")),
  levels = c("low", "medium", "high"))
HMDA$mhist <- as.numeric(HMDA$mhist)
HMDA$chist <- as.numeric(HMDA$chist)

# calculate and store regression results with probit model
probit.11.4 <- glm(deny ~ afam + pirat + hirat + lvrat + chist + mhist + phist 
                  + insurance + selfemp, data = HMDA, family = binomial(link = "probit"))

# summarize regression results
#summary(probit.11.4)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("HMDA")

# adjust variables for regression
HMDA$lvrat <- factor(
  ifelse(HMDA$lvrat < 0.8, "low",
  ifelse(HMDA$lvrat >= 0.8 & HMDA$lvrat <= 0.95, "medium", "high")),
  levels = c("low", "medium", "high"))
HMDA$mhist <- as.numeric(HMDA$mhist)
HMDA$chist <- as.numeric(HMDA$chist)

# calculate and store regression results with probit model
probit.11.4 <- glm(deny ~ afam + pirat + hirat + lvrat + chist + mhist + phist 
                  + insurance + selfemp, data = HMDA, family = binomial(link = "probit"))

# summarize regression results
summary(probit.11.4)
```


<!--..........................................................................-->
## STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<!--..........................................................................-->
### Logit {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/hmda_sw.dta

# adjust variables for regression
gen afam= (s13==3)
gen mhist = s42
gen chist = s43
gen phist = (s44>0)
gen insurance = (s53==1)
gen selfemp = (s27a==1)
gen deny= (s7==3)
gen hirat= s45/100
gen pirat= s46/100
gen lvrat = s6/s50
gen lvratmedium = (lvrat>=0.80)*(lvrat<=0.95)
gen lvrathigh = (lvrat>0.95) 


# calculate and show regression results with logit model
logit deny afam pirat hirat lvratmedium lvrathigh chist mhist phist insurance selfemp
```

<p class="head02">
Output 
</p>


<pre>

Iteration 0:   log likelihood =  -872.0853  
Iteration 1:   log likelihood = -672.05096  
Iteration 2:   log likelihood = -656.94676  
Iteration 3:   log likelihood = -636.05789  
Iteration 4:   log likelihood = -635.63857  
Iteration 5:   log likelihood = -635.63667  
Iteration 6:   log likelihood = -635.63667  

Logistic regression                             Number of obs     =      2,380
                                                LR chi2(10)       =     472.90
                                                Prob > chi2       =     0.0000
Log likelihood = -635.63667                     Pseudo R2         =     0.2711

------------------------------------------------------------------------------
        deny |      Coef.   Std. Err.      z    P>|z|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
        afam |   .6884231   .1773918     3.88   0.000     .3407416    1.036105
       pirat |   4.764416   1.042587     4.57   0.000     2.720983     6.80785
       hirat |  -.1088114   1.239403    -0.09   0.930    -2.537996    2.320374
 lvratmedium |    .463525    .159096     2.91   0.004     .1517025    .7753475
   lvrathigh |   1.494764   .3112213     4.80   0.000     .8847812    2.104746
       chist |   .2903017   .0398178     7.29   0.000     .2122603    .3683431
       mhist |   .2790178   .1399192     1.99   0.046     .0047811    .5532544
       phist |   1.225797   .2054334     5.97   0.000     .8231547    1.628439
   insurance |   4.548166   .5524863     8.23   0.000     3.465312    5.631019
     selfemp |   .6661288   .2115319     3.15   0.002     .2515338    1.080724
       _cons |  -5.707384   .4097911   -13.93   0.000    -6.510559   -4.904208
------------------------------------------------------------------------------

</pre>

<!--..........................................................................-->
### Probit {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/hmda_sw.dta

# adjust variables for regression
gen afam= (s13==3)
gen mhist = s42
gen chist = s43
gen phist = (s44>0)
gen insurance = (s53==1)
gen selfemp = (s27a==1)
gen deny= (s7==3)
gen hirat= s45/100
gen pirat= s46/100
gen lvrat = s6/s50
gen lvratmedium = (lvrat>=0.80)*(lvrat<=0.95)
gen lvrathigh = (lvrat>0.95) 


# calculate and show regression results with logit model
probit deny afam pirat hirat lvratmedium lvrathigh chist mhist phist insurance selfemp
```

<p class="head02">
Output 
</p>


<pre>

Iteration 0:   log likelihood =  -872.0853  
Iteration 1:   log likelihood = -643.92086  
Iteration 2:   log likelihood = -636.87532  
Iteration 3:   log likelihood = -636.84706  
Iteration 4:   log likelihood = -636.84706  

Probit regression                               Number of obs     =      2,380
                                                LR chi2(10)       =     470.48
                                                Prob > chi2       =     0.0000
Log likelihood = -636.84706                     Pseudo R2         =     0.2697

------------------------------------------------------------------------------
        deny |      Coef.   Std. Err.      z    P>|z|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
        afam |   .3891261   .0966749     4.03   0.000     .1996468    .5786054
       pirat |   2.441787   .5279727     4.62   0.000     1.406979    3.476594
       hirat |  -.1846764   .6519372    -0.28   0.777     -1.46245    1.093097
 lvratmedium |   .2139677   .0819881     2.61   0.009      .053274    .3746614
   lvrathigh |   .7910831   .1744755     4.53   0.000     .4491174    1.133049
       chist |   .1546224   .0214869     7.20   0.000     .1125089     .196736
       mhist |   .1477082   .0735792     2.01   0.045     .0034956    .2919209
       phist |   .6974496   .1190143     5.86   0.000     .4641859    .9307134
   insurance |   2.556796   .2814955     9.08   0.000     2.005075    3.108517
     selfemp |   .3586252     .11169     3.21   0.001     .1397168    .5775336
       _cons |  -3.040568   .2014292   -15.09   0.000    -3.435362   -2.645774
------------------------------------------------------------------------------

</pre>

<!--..........................................................................-->
<!--..........................................................................-->

## References

<hr />

<p class="head01">
References
</p>

<!--##########################################################################-->
<!-- THIS IS THE END --> 
<script>
var coll = document.getElementsByClassName("collapsible01");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>

<script>
var coll = document.getElementsByClassName("collapsible02");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>