---
title: "Introductory Econometrics"
subtitle: "*R* and *STATA* Code"
author: by Markus Mößler and Marc Bachmeier
output:
  html_document:
    highlight: tango
    css: style.css
    includes:
      in_header: logo.html
bibliography: [Teaching_References.bib]
biblio-style: apalike
link-citations: yes
nocite: | 
  @StockWatson2020Introduction
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Cross-Sectional Data | Estimation {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 6.2 
</p>

The dataset contains data on test performance, school characteristics and student demographic backgrounds for school districts in California with 420 observations on 14 variables. We calculate a linear regression with the average math and reading score as the dependent variable. 

| Variable name | Description   |
| ------------- |:-----------------------:|
| read          | Average reading score |
| math          | Average math score      |
| english       | Percent of English learners      |
| students      | Total enrollment      |
| teachers      | Number of teachers   |


<hr />

<!--..........................................................................-->
## *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.6.1 <- lm(score ~ str + english, data = CASchools)

# summarize regression results
summary(lm.6.1)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.6.1 <- lm(score ~ str + english, data = CASchools)

# summarize regression results
summary(lm.6.1)
```

<!--..........................................................................-->
## STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/caschool.dta
 
# rename variables
rename el_pct english
rename testscr score

# calculate and show regression results
reg score str english
```

<p class="head02">
Output 
</p>


<pre>

      Source |       SS           df       MS      Number of obs   =       420
-------------+----------------------------------   F(2, 417)       =    155.01
       Model |  64864.3011         2  32432.1506   Prob > F        =    0.0000
    Residual |  87245.2925       417  209.221325   R-squared       =    0.4264
-------------+----------------------------------   Adj R-squared   =    0.4237
       Total |  152109.594       419  363.030056   Root MSE        =    14.464

------------------------------------------------------------------------------
       score |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
         str |  -1.101296   .3802783    -2.90   0.004    -1.848797   -.3537945
     english |  -.6497768   .0393425   -16.52   0.000    -.7271112   -.5724423
       _cons |   686.0322   7.411312    92.57   0.000     671.4641    700.6004
------------------------------------------------------------------------------

</pre>


<!--..........................................................................-->
## Gretl {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Data
</p>

You can download and install the data sets from the Stock and Watson textbook from the following link: 
http://gretl.sourceforge.net/gretl_data.html \
The data sets are automatically saved in the Gretl folder under data. Alternatively, another storage location can be selected. Afterwards the data sets can easily be opened via the script with the command open. Alternatively, under the tab file, Open data can be selected and from the folder in which the data sets were stored the desired data set can be selected.

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
open caschool.gdt

# rename variables
rename el_pct english
rename testscr score

# calculate and show regression results
ols score 0 str english
```

<p class="head02">
Output 
</p>


<pre>

Model 1: OLS, using observations 1-420
Dependent variable: score

             coefficient   std. error   t-ratio    p-value 
  ---------------------------------------------------------
  const      686.032       7.41131       92.57    3.87e-280 ***
  str         −1.10130     0.380278      −2.896   0.0040    ***
  english     −0.649777    0.0393425    −16.52    1.66e-047 ***

Mean dependent var   654.1565   S.D. dependent var   19.05335
Sum squared resid    87245.29   S.E. of regression   14.46448
R-squared            0.426431   Adjusted R-squared   0.423680
F(2, 417)            155.0136   P-value(F)           4.62e-51
Log-likelihood      −1716.561   Akaike criterion     3439.123
Schwarz criterion    3451.243   Hannan-Quinn         3443.913

</pre>



<!--..........................................................................-->
<!--..........................................................................-->

## References

<hr />

<p class="head01">
References
</p>

<!--##########################################################################-->
<!-- THIS IS THE END --> 
<script>
var coll = document.getElementsByClassName("collapsible01");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>

<script>
var coll = document.getElementsByClassName("collapsible02");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>