---
title: "Introductory Econometrics"
subtitle: "*R* and *STATA* Code"
author: by Markus Mößler and Marc Bachmeier
output:
  html_document:
    highlight: tango
    css: style.css
    includes:
      in_header: logo.html
bibliography: [Teaching_References.bib]
biblio-style: apalike
link-citations: yes
nocite: | 
  @StockWatson2020Introduction
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Cross-Sectional Data | Estimation {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 6.2 
</p>

The dataset contains data on test performance, school characteristics and student demographic backgrounds for school districts in California with 420 observations on 14 variables. We calculate a linear regression with the average math and reading score as the dependent variable. 

| Variable name | Description   |
| ------------- |:-----------------------:|
| read          | Average reading score |
| math          | Average math score      |
| english       | Percent of English learners      |
| students      | Total enrollment      |
| teachers      | Number of teachers   |


<hr />

<!--..........................................................................-->
## *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.6.1 <- lm(score ~ str + english, data = CASchools)

# summarize regression results
summary(lm.6.1)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessarry 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CASchools")

# generate new variables for regression
CASchools$str <- CASchools$students/CASchools$teachers       
CASchools$score <- (CASchools$read + CASchools$math)/2

# calculate and store regression results
lm.6.1 <- lm(score ~ str + english, data = CASchools)

# summarize regression results
summary(lm.6.1)
```

<!--..........................................................................-->
## STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/caschool.dta
 
# rename variables
rename el_pct english
rename testscr score

# calculate and show regression results
reg score str english
```

<p class="head02">
Output 
</p>


<pre>

      Source |       SS           df       MS      Number of obs   =       420
-------------+----------------------------------   F(2, 417)       =    155.01
       Model |  64864.3011         2  32432.1506   Prob > F        =    0.0000
    Residual |  87245.2925       417  209.221325   R-squared       =    0.4264
-------------+----------------------------------   Adj R-squared   =    0.4237
       Total |  152109.594       419  363.030056   Root MSE        =    14.464

------------------------------------------------------------------------------
       score |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
         str |  -1.101296   .3802783    -2.90   0.004    -1.848797   -.3537945
     english |  -.6497768   .0393425   -16.52   0.000    -.7271112   -.5724423
       _cons |   686.0322   7.411312    92.57   0.000     671.4641    700.6004
------------------------------------------------------------------------------

</pre>


<!--..........................................................................-->
<!--..........................................................................-->

## References

<hr />

<p class="head01">
References
</p>

<!--##########################################################################-->
<!-- THIS IS THE END --> 
<script>
var coll = document.getElementsByClassName("collapsible01");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>

<script>
var coll = document.getElementsByClassName("collapsible02");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>