---
title: "Introductory Econometrics"
subtitle: "*R* and *STATA* Code"
author: by Markus Mößler and Marc Bachmeier
output:
  html_document:
    highlight: tango
    css: style.css
    includes:
      in_header: logo.html
bibliography: [Teaching_References.bib]
biblio-style: apalike
link-citations: yes
nocite: | 
  @StockWatson2020Introduction
---

<!--..........................................................................-->
<!--..........................................................................-->

```{r,include=FALSE}
knitr::opts_chunk$set(
  include = TRUE,
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8)
options(scipen=1)
```

```{r,klippy, echo=FALSE, include=TRUE}
#See: https://rlesur.github.io/klippy/articles/klippy.html
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done', position = c('top', 'right'))
```

<!--..........................................................................-->
<!--..........................................................................-->

<hr />

<!--..........................................................................-->
# Regression Analysis with Cross-Sectional Data | Instrumental Variable {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head01">
Chapter 12.4 
</p>

Panel data on cigarette consumption for the 48 continental US States from 1985–1995 contains 48 observations on 7 variables fpr 2 periods. We calculate a linear regression with the change in cigarette consumption as the dependent variable. Additionally we use the difference in the sales taxes between 1985 and 1995 and the difference in the cigarette-specific sales taxes between 1985 and 1995 as instruments for the price difference between 1985 and 1995.

| Variable name | Description   |
| ------------- |:-----------------------:|
| packs         | Number of packs per capita |
| price         | Average price during fiscal year, including sales tax     |
| income        | State personal income (total, nominal)    |
| cpi           | Consumer price index  |
| population    | State population |
| taxs          | Average excise taxes for fiscal year, including sales tax    |
| tax           | Average state, federal and average local excise taxes for fiscal year     |


<hr />

<!--..........................................................................-->
## *R* Sofware {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,results='hide'}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CigarettesSW")

c1985 <- subset(CigarettesSW, year== "1985")
c1995 <- subset(CigarettesSW, year== "1995")

# generate new variables for regression
packsdiff <- log(c1995$packs) - log(c1985$packs)
pricediff <- log(c1995$price/c1995$cpi) - log(c1985$price/c1985$cpi)
incomediff <- log(c1995$income/c1995$population/c1995$cpi) - log(c1985$income/c1985$population/c1985$cpi)
salestaxdiff <- (c1995$taxs - c1995$tax)/c1995$cpi - (c1985$taxs - c1985$tax)/c1985$cpi
cigtaxdiff <- c1995$tax/c1995$cpi - c1985$tax/c1985$cpi

# calculate and store regression results with instrumental variable
cig_ivreg <- ivreg(packsdiff ~ pricediff + incomediff | incomediff + salestaxdiff + cigtaxdiff, data = CigarettesSW)

# summarize regression results
summary(cig_ivreg)
```

<hr />

<p class="head02">
Output 
</p>

```{r,echo=FALSE}
# install package with data sets if necessary 
# install.packages("AER")

# load package with data sets
library("AER")

# load data set for regression
data("CigarettesSW")

c1985 <- subset(CigarettesSW, year== "1985")
c1995 <- subset(CigarettesSW, year== "1995")

# generate new variables for regression
packsdiff <- log(c1995$packs) - log(c1985$packs)
pricediff <- log(c1995$price/c1995$cpi) - log(c1985$price/c1985$cpi)
incomediff <- log(c1995$income/c1995$population/c1995$cpi) - log(c1985$income/c1985$population/c1985$cpi)
salestaxdiff <- (c1995$taxs - c1995$tax)/c1995$cpi - (c1985$taxs - c1985$tax)/c1985$cpi
cigtaxdiff <- c1995$tax/c1995$cpi - c1985$tax/c1985$cpi

# calculate and store regression results with instrumental variable
cig_ivreg <- ivreg(packsdiff ~ pricediff + incomediff | incomediff + salestaxdiff + cigtaxdiff, data = CigarettesSW)

# summarize regression results
summary(cig_ivreg)
```

<!--..........................................................................-->
## STATA {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
use http://fmwww.bc.edu/ec-p/data/stockwatson/cig_ch10.dta

# reshape data
reshape wide cpi pop packpc income tax avgprs taxs, i(state) j(year)

# generate new variables for regression
gen packsdiff= log(packpc1995) - log(packpc1985)
gen pricediff= log(avgprs1995/cpi1995) - log(avgprs1985/cpi1985)
gen incomediff= log(income1995/pop1995/cpi1995) - log(income1985/pop1985/cpi1985)
gen salestaxdiff= (taxs1995 - tax1995) / cpi1995 - (taxs1985 - tax1985) / cpi1985
gen cigtaxdiff= tax1995 / cpi1995 - tax1985 / cpi1985

# calculate and show regression results with instrumental variable
ivreg packsdiff (pricediff = salestaxdiff cigtaxdiff) incomediff
```

<p class="head02">
Output 
</p>


<pre>

      Source |       SS           df       MS      Number of obs   =        48
-------------+----------------------------------   F(2, 45)        =     27.71
       Model |  .451735013         2  .225867506   Prob > F        =    0.0000
    Residual |  .374721452        45  .008327143   R-squared       =    0.5466
-------------+----------------------------------   Adj R-squared   =    0.5264
       Total |  .826456465        47   .01758418   Root MSE        =    .09125

------------------------------------------------------------------------------
   packsdiff |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
   pricediff |  -1.202403   .1711928    -7.02   0.000    -1.547203   -.8576033
  incomediff |   .4620301   .3081013     1.50   0.141    -.1585177    1.082578
       _cons |  -.0520034   .0604947    -0.86   0.395    -.1738459    .0698391
------------------------------------------------------------------------------
Instrumented:  pricediff
Instruments:   incomediff salestaxdiff cigtaxdiff
------------------------------------------------------------------------------

</pre>


<!--..........................................................................-->
## Gretl {.tabset .tabset-fade}
<!--..........................................................................-->

<hr />

<p class="head02">
Data
</p>

You can download and install the data sets from the Stock and Watson textbook from the following link: 
http://gretl.sourceforge.net/gretl_data.html \
The data sets are automatically saved in the Gretl folder under data. Alternatively, another storage location can be selected. Afterwards the data sets can easily be opened via the script with the command open. Alternatively, under the tab file, Open data can be selected and from the folder in which the data sets were stored the desired data set can be selected.

<p class="head02">
Code 
</p>

```{r,eval=FALSE}
# load data set for regression
open cig_ch10.gdt

# generate new variables for regression
genr packsdiff = log(packpc) - log(packpc(-1))
genr pricediff = log(avgprs/cpi) - log(avgprs(-1)/cpi(-1))
genr incomediff = log(income/pop/cpi) - log(income(-1)/pop(-1)/cpi(-1))
genr salestaxdiff = (taxs - tax)/cpi - (taxs(-1) - tax(-1))/cpi(-1)
genr cigtaxdiff = tax/cpi - tax(-1)/cpi(-1)

# calculate and show regression results with instrumental variables
tsls packsdiff 0 pricediff incomediff ; 0 salestaxdiff cigtaxdiff incomediff
```

<p class="head02">
Output 
</p>


<pre>

Model 1: TSLS, using 48 observations
Dependent variable: packsdiff
Instrumented: pricediff 
Instruments: const salestaxdiff cigtaxdiff incomediff 

               coefficient   std. error   t-ratio   p-value 
  ----------------------------------------------------------
  const        −0.0520034    0.0604947    −0.8596   0.3945  
  pricediff    −1.20240      0.171193     −7.024    9.40e-09 ***
  incomediff    0.462030     0.308101      1.500    0.1407  

Mean dependent var  −0.251449   S.D. dependent var   0.132605
Sum squared resid    0.374721   S.E. of regression   0.091253
R-squared            0.555279   Adjusted R-squared   0.535513
F(2, 45)             27.70604   P-value(F)           1.44e-08

Log-likelihood for packpc = 61.0558

Hausman test -
  Null hypothesis: OLS estimates are consistent
  Asymptotic test statistic: Chi-square(1) = 3.81981
  with p-value = 0.0506501

Sargan over-identification test -
  Null hypothesis: all instruments are valid
  Test statistic: LM = 4.83805
  with p-value = P(Chi-square(1) > 4.83805) = 0.0278384

Weak instrument test - 
  First-stage F-statistic (2, 44) = 75.6526
  Critical values for desired TSLS maximal size, when running
  tests at a nominal 5% significance level:

     size      10%      15%      20%      25%
    value    19.93    11.59     8.75     7.25

  Maximal size is probably less than 10%

</pre>



<!--..........................................................................-->
<!--..........................................................................-->

## References

<hr />

<p class="head01">
References
</p>

<!--##########################################################################-->
<!-- THIS IS THE END --> 
<script>
var coll = document.getElementsByClassName("collapsible01");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>

<script>
var coll = document.getElementsByClassName("collapsible02");
var i;

for (i = 0; i < coll.length; i++) {
  coll[i].addEventListener("click", function() {
    this.classList.toggle("active");
    var content = this.nextElementSibling;
    if (content.style.display === "block") {
      content.style.display = "none";
    } else {
      content.style.display = "block";
    }
  });
}
</script>