---
output: html_fragment
bibliography: [Ma_EconometricMethods_Literature.bib]
biblio-style: apalike
link-citations: no
nocite: | 
  @StockWatson2019Introduction
---

<!--..........................................................................-->
<!--..........................................................................-->

<!-- Include header -->

````{=html}
```{r, echo=FALSE, results='asis'}
xfun::file_string('header_02.html')
```
````

<!--..........................................................................-->
<!--..........................................................................-->

<!--..........................................................................-->
<hr />

# Approach

This Learning Module contains the implementation of the empirical analysis of @StockWatson2020Introduction in <span class="emp01">R</span>, <span class="emp01">STATA</span> and <span class="emp01">gretl</span>.

<!--
This is an overview of the most important function of *R* and STATA necessary to implement basic econometric methods.
-->

Use the links below to get to the implementation of the respective Chapter/Empirical model.

<!--..........................................................................-->
<hr />

# Chapter/Empirical model

<!-- 0. Installation of *R* ([GoTo](./00_InstallationOfR/00_InstallationOfR_XX.html)) -->
1. Regression Analysis with Cross-Sectional Data: [Estimation](./01_Section/01_Section_XX.html)
2. Regression Analysis with Cross-Sectional Data: [Inference](./02_Section/02_Section_XX.html)
3. Regression Analysis with Cross-Sectional Data: [Heteroskedasticity](./03_Section/03_Section_XX.html)
4. Regression Analysis with Panel-Data: [Fixed and random effects](./06_Section/06_Section_XX.html) 
5. Regression Analysis with Cross-Sectional Data: [Limited Dependent Variable](./05_Section/05_Section_XX.html)
6. Regression Analysis with Cross-Sectional Data: [Instrumental Variable](./04_Section/04_Section_XX.html)

<!-- 4. Regression Analysis with Cross-Sectional Data: [Instrumental Variable](./04_Section/04_Section_XX.html) -->
<!-- 5. Regression Analysis with Cross-Sectional Data: [Limited Dependent Variable](./05_Section/05_Section_XX.html) -->
<!-- 6. Regression Analysis with Panel-Data: [Fixed and random effects](./06_Section/06_Section_XX.html) -->

<!--..........................................................................-->
<hr />

# Using Gretl IDE

1. Introduction: [Link](./Gretl_IDE/01_Introduction/01_Introduction_XX.html)
2. Data manipulation: [Link](./Gretl_IDE/02_DataManipulation/02_DataManipulation_XX.html)
3. Regression analysis: [Link](./Gretl_IDE/03_Regression/03_Regression_XX.html)
4. Output generation in GRETL: [Link](./Gretl_IDE/04_Output/04_Output_XX.html)
5. Panel data analysis: [Link](./Gretl_IDE/05_PanelData/05_PanelData_XX.html)
6. Time series: [Link](./Gretl_IDE/06_TimeSeries/06_TimeSeries_XX.html)
<!--..........................................................................-->
<hr />

# Literature

<div id="refs"></div>

<!--..........................................................................-->
<hr />

<p class="back01">
[Back To *Start Practical Class*](../index.html)
</p>

<!--..........................................................................-->
<hr />





<!--..........................................................................--> 
<!-- THIS IS THE END --> 

<!-- Include bottom -->

````{=html}
```{r, include=TRUE, echo=FALSE, results='asis'}
xfun::file_string('bottom_01.html')
```
````